---
title: "Green Space Working Code"
author: "Laura Mackenzie"
date: "3/24/2021"
output:
   pdf_document: default
  html_document: default
  github_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
#Loading in libraries 
library(dplyr)
library(tidyverse)
library(readr)
library(readxl)
library(ggplot2)
install.packages("wordcloud")
library(wordcloud)
install.packages("RColorBrewer")
library(RColorBrewer)
install.packages("wordcloud2")
library(wordcloud2)
install.packages("tm")
library(tm)
library(tmap)
install.packages("ggwordcloud")
library(ggwordcloud)
install.packages("devtools")
library(devtools)
install.packages("likert")
library(likert)
install.packages("sqldf")
library(sqldf)
library(png)
library(raster)
library(tmap)
library(sp)
install.packages("survey")
library(survey)
install.packages("jtools")
library(jtools)
```

```{r}
#raw_frame<- read_csv(".csv")

#anonymous_frame<- raw_frame %>% 
  #filter(DistributionChannel == "anonymous")%>% dplyr::select ( "Q3","Q4","Q5","Q6","Q6_15_TEXT","Q7","Q8","Q9","Q10","Q10_14_TEXT","Q11","Q12","Q13","Q14","Q15","Q16","Q17","Q18","Q19","Q20","Q20_8_TEXT","Q21","Q21_5_TEXT","Q22","Q23","Q24","Q25","Q26","Q27","Q28","Q29","Q30","Q31","Q32","Q33","Q34","Q35", "Q36", "Q37","Q37_6_TEXT","Q38","Q38.5", "Q39","Q39.5", "Q40","Q41","Q49","Q42","Q43","Q44","Q45","Q45_3_TEXT","Q46","Q47","Q48")

```
# UC Berkeley, CA NDVI (5 mile radius)

```{r}
# import the naip pre-fire data
naip_multispectral_br5 <- stack("~/GreenSpace_Thesis/Google Earth Images/UC Berkeley 5 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_br5 <- brick(naip_multispectral_br5)

# calculate ndvi with naip
naip_multispectral_br5[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_br5 <- (naip_multispectral_br5[[4]] - naip_multispectral_br5[[1]]) / (naip_multispectral_br5[[4]] + naip_multispectral_br5[[1]])

# plot the data
plot(naip_ndvi_br5,
     main = "NDVI of UC Berkeley, CA 5 mile",
     axes = FALSE, box = FALSE)
```

```{r}
# view distribution of NDVI values
hist(naip_ndvi_br5,
  main = "NDVI: Distribution of pixels\n NAIP 2018 UC Berkeley,CA 5 mile",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

\newpage

# UC Berkeley, CA NDVI (1 mile radius)

```{r}
# import the naip pre-fire data
naip_multispectral_br1 <- stack("~/GreenSpace_Thesis/Google Earth Images/UC Berkeley 1 mile.png")

# convert data into rasterbrick for faster processing
naip_multispectral_br1 <- brick(naip_multispectral_br1)

# calculate ndvi with naip
naip_multispectral_br1[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_br1 <- (naip_multispectral_br1[[4]] - naip_multispectral_br1[[1]]) / (naip_multispectral_br1[[4]] + naip_multispectral_br1[[1]])

# plot the data
plot(naip_ndvi_br1,
     main = "NDVI of UC Berkeley, CA (1 mile radius)",
     axes = FALSE, box = FALSE)
```

```{r}
# view distribution of NDVI values
hist(naip_ndvi_br1,
  main = "NDVI: Distribution of pixels\n NAIP 2018 UC Berkeley,CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

# El CErrito 1 mile 

```{r}
# import the naip pre-fire data
naip_multispectral_elc <- stack("~/GreenSpace_Thesis/Google Earth Images/El Cerrito 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_elc <- brick(naip_multispectral_elc)

# calculate ndvi with naip
naip_multispectral_elc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_elc <- (naip_multispectral_elc[[4]] - naip_multispectral_elc[[1]]) / (naip_multispectral_elc[[4]] + naip_multispectral_elc[[1]])

# plot the data
plot(naip_ndvi_elc,
     main = "NDVI of El Cerrito, CA 1 mile",
     axes = FALSE, box = FALSE)
```

```{r}
# view distribution of NDVI values
hist(naip_ndvi_elc,
  main = "NDVI: Distribution of pixels\n NAIP 2018 El CErrito,CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_slc <- stack("~/GreenSpace_Thesis/Google Earth Images/Shenyang, Liaoning, China 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_slc <- brick(naip_multispectral_slc)

# calculate ndvi with naip
naip_multispectral_slc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_slc <- (naip_multispectral_slc[[4]] - naip_multispectral_slc[[1]]) / (naip_multispectral_slc[[4]] + naip_multispectral_slc[[1]])

# plot the data
plot(naip_ndvi_slc,
     main = "NDVI of Shenyang, Liaoning, China 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slc,
  main = "NDVI: Distribution of pixels\n NAIP Shenyang, Liaoning, China (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_blm <- stack("~/GreenSpace_Thesis/Google Earth Images/Billingstad, Norway 1mi.png")
# convert data into rasterbrick for faster processing

naip_multispectral_blm <- brick(naip_multispectral_blm)

# calculate ndvi with naip
naip_multispectral_blm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_blm <- (naip_multispectral_blm[[4]] - naip_multispectral_blm[[1]]) / (naip_multispectral_blm[[4]] + naip_multispectral_blm[[1]])

# plot the data
plot(naip_ndvi_blm,
     main = "NDVI of Billingstad, Norway 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slc,
  main = "NDVI: Distribution of pixels\n NAIP Billigstad, Norway (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_hny <- stack("~/GreenSpace_Thesis/Google Earth Images/Harlem, NY 1mi.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hny <- brick(naip_multispectral_hny)

# calculate ndvi with naip
naip_multispectral_hny[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hny <- (naip_multispectral_hny[[4]] - naip_multispectral_hny[[1]]) / (naip_multispectral_hny[[4]] + naip_multispectral_hny[[1]])

# plot the data
plot(naip_ndvi_hny,
     main = "NDVI of Harlem, New York 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slc,
  main = "NDVI: Distribution of pixels\n NAIP Harlem, New York (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_poca <- stack("~/GreenSpace_Thesis/Google Earth Images/Poway, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_poca <- brick(naip_multispectral_poca)

# calculate ndvi with naip
naip_multispectral_poca[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_poca <- (naip_multispectral_poca[[4]] - naip_multispectral_poca[[1]]) / (naip_multispectral_poca[[4]] + naip_multispectral_poca[[1]])

# plot the data
plot(naip_ndvi_poca,
     main = "NDVI of Poway, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_poca,
  main = "NDVI: Distribution of pixels\n NAIP Poway, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_scca <- stack("~/GreenSpace_Thesis/Google Earth Images/San Clemente, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_scca <- brick(naip_multispectral_scca)

# calculate ndvi with naip
naip_multispectral_scca[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_scca <- (naip_multispectral_scca[[4]] - naip_multispectral_scca[[1]]) / (naip_multispectral_scca[[4]] + naip_multispectral_scca[[1]])

# plot the data
plot(naip_ndvi_scca,
     main = "NDVI of San Clemente, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_poca,
  main = "NDVI: Distribution of pixels\n NAIP San Clemente, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_un <- stack("~/GreenSpace_Thesis/Google Earth Images/Union City, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_un <- brick(naip_multispectral_un)

# calculate ndvi with naip
naip_multispectral_un[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_un <- (naip_multispectral_un[[4]] - naip_multispectral_un[[1]]) / (naip_multispectral_un[[4]] + naip_multispectral_un[[1]])

# plot the data
plot(naip_ndvi_un,
     main = "NDVI of Union City, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_un,
  main = "NDVI: Distribution of pixels\n NAIP Union City, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_ado <- stack("~/GreenSpace_Thesis/Google Earth Images/Adelanto, CA 1 mile .png")
# convert data into rasterbrick for faster processing

naip_multispectral_ado <- brick(naip_multispectral_ado)

# calculate ndvi with naip
naip_multispectral_ado[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ado <- (naip_multispectral_ado[[4]] - naip_multispectral_ado[[1]]) / (naip_multispectral_ado[[4]] + naip_multispectral_ado[[1]])

# plot the data
plot(naip_ndvi_ado,
     main = "NDVI of Adelanto, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ado,
  main = "NDVI: Distribution of pixels\n NAIP Adelanto, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_adie <- stack("~/GreenSpace_Thesis/Google Earth Images/Adikeih, Eritrea 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_adie <- brick(naip_multispectral_adie)

# calculate ndvi with naip
naip_multispectral_adie[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_adie <- (naip_multispectral_adie[[4]] - naip_multispectral_adie[[1]]) / (naip_multispectral_adie[[4]] + naip_multispectral_adie[[1]])

# plot the data
plot(naip_ndvi_adie,
     main = "NDVI of Adikeih, Eritrea 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_adie,
  main = "NDVI: Distribution of pixels\n NAIP Adikeih, Eritrea (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_ala <- stack("~/GreenSpace_Thesis/Google Earth Images/Alameda, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ala <- brick(naip_multispectral_ala)

# calculate ndvi with naip
naip_multispectral_ala[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ala <- (naip_multispectral_ala[[4]] - naip_multispectral_ala[[1]]) / (naip_multispectral_ala[[4]] + naip_multispectral_ala[[1]])

# plot the data
plot(naip_ndvi_ala,
     main = "NDVI of Alameda, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ala,
  main = "NDVI: Distribution of pixels\n NAIP Alameda, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_alamo <- stack("~/GreenSpace_Thesis/Google Earth Images/Alamo, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_alamo <- brick(naip_multispectral_alamo)

# calculate ndvi with naip
naip_multispectral_alamo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_alamo <- (naip_multispectral_alamo[[4]] - naip_multispectral_alamo[[1]]) / (naip_multispectral_alamo[[4]] + naip_multispectral_alamo[[1]])

# plot the data
plot(naip_ndvi_alamo,
     main = "NDVI of Alamo, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ala,
  main = "NDVI: Distribution of pixels\n NAIP Alamo, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_alb <- stack("~/GreenSpace_Thesis/Google Earth Images/Albany, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_alb <- brick(naip_multispectral_alb)

# calculate ndvi with naip
naip_multispectral_alb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_alb <- (naip_multispectral_alb[[4]] - naip_multispectral_alb[[1]]) / (naip_multispectral_alb[[4]] + naip_multispectral_alb[[1]])

# plot the data
plot(naip_ndvi_alb,
     main = "NDVI of Albany, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_alb,
  main = "NDVI: Distribution of pixels\n NAIP Albany, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_alh <- stack("~/GreenSpace_Thesis/Google Earth Images/Alhambra, CA 1 mile .png")
# convert data into rasterbrick for faster processing

naip_multispectral_alh <- brick(naip_multispectral_alh)

# calculate ndvi with naip
naip_multispectral_alh[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_alh <- (naip_multispectral_alh[[4]] - naip_multispectral_alh[[1]]) / (naip_multispectral_alh[[4]] + naip_multispectral_alh[[1]])

# plot the data
plot(naip_ndvi_alh,
     main = "NDVI of Alhambra, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_alh,
  main = "NDVI: Distribution of pixels\n NAIP Alhambra, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_alta <- stack("~/GreenSpace_Thesis/Google Earth Images/Altadena, CA 1 mile .png")
# convert data into rasterbrick for faster processing

naip_multispectral_alta <- brick(naip_multispectral_alta)

# calculate ndvi with naip
naip_multispectral_alta[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_alta <- (naip_multispectral_alta[[4]] - naip_multispectral_alta[[1]]) / (naip_multispectral_alta[[4]] + naip_multispectral_alta[[1]])

# plot the data
plot(naip_ndvi_alta,
     main = "NDVI of Altadena, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_alta,
  main = "NDVI: Distribution of pixels\n NAIP Altadena, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_ana <- stack("~/GreenSpace_Thesis/Google Earth Images/Anaheim, CA 1 mile .png")
# convert data into rasterbrick for faster processing

naip_multispectral_ana <- brick(naip_multispectral_ana)

# calculate ndvi with naip
naip_multispectral_ana[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ana <- (naip_multispectral_ana[[4]] - naip_multispectral_ana[[1]]) / (naip_multispectral_ana[[4]] + naip_multispectral_ana[[1]])

# plot the data
plot(naip_ndvi_ana,
     main = "NDVI of Anaheim, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ana,
  main = "NDVI: Distribution of pixels\n NAIP Anaheim, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_ap <- stack("~/GreenSpace_Thesis/Google Earth Images/Apple Valley, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ap <- brick(naip_multispectral_ap)

# calculate ndvi with naip
naip_multispectral_ap[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ap <- (naip_multispectral_ap[[4]] - naip_multispectral_ap[[1]]) / (naip_multispectral_ap[[4]] + naip_multispectral_ap[[1]])

# plot the data
plot(naip_ndvi_ap,
     main = "NDVI of Apple Valley, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ap,
  main = "NDVI: Distribution of pixels\n NAIP Apple Valley, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_temp <- stack("~/GreenSpace_Thesis/Google Earth Images/Temple City, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_temp <- brick(naip_multispectral_temp)

# calculate ndvi with naip
naip_multispectral_temp[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_temp <- (naip_multispectral_temp[[4]] - naip_multispectral_temp[[1]]) / (naip_multispectral_temp[[4]] + naip_multispectral_temp[[1]])

# plot the data
plot(naip_ndvi_temp,
     main = "NDVI of Temple City, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_temp,
  main = "NDVI: Distribution of pixels\n NAIP Temple City, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_aus <- stack("~/GreenSpace_Thesis/Google Earth Images/Austin, TX 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_aus <- brick(naip_multispectral_aus)

# calculate ndvi with naip
naip_multispectral_aus[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_aus <- (naip_multispectral_aus[[4]] - naip_multispectral_aus[[1]]) / (naip_multispectral_aus[[4]] + naip_multispectral_aus[[1]])

# plot the data
plot(naip_ndvi_aus,
     main = "NDVI of Austin, TX 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_aus,
  main = "NDVI: Distribution of pixels\n NAIP Austin, TX (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_bagph <- stack("~/GreenSpace_Thesis/Google Earth Images/Baguio, Benguet, Philippines 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bagph <- brick(naip_multispectral_bagph)

# calculate ndvi with naip
naip_multispectral_bagph[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bagph <- (naip_multispectral_bagph[[4]] - naip_multispectral_bagph[[1]]) / (naip_multispectral_bagph[[4]] + naip_multispectral_bagph[[1]])

# plot the data
plot(naip_ndvi_bagph,
     main = "NDVI of Baguio City, Benguet, Philippines 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bagph,
  main = "NDVI: Distribution of pixels\n NAIP Baguio City, Benguet, Philippines (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_bak <- stack("~/GreenSpace_Thesis/Google Earth Images/Bakersfeild 10 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bak <- brick(naip_multispectral_bak)

# calculate ndvi with naip
naip_multispectral_bak[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bak <- (naip_multispectral_bak[[4]] - naip_multispectral_bak[[1]]) / (naip_multispectral_bak[[4]] + naip_multispectral_bak[[1]])

# plot the data
plot(naip_ndvi_bak,
     main = "NDVI of Bakersfeild, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bak,
  main = "NDVI: Distribution of pixels\n NAIP Bakersfeild (10 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_bang <- stack("~/GreenSpace_Thesis/Google Earth Images/Bangkok, Thailand 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bang <- brick(naip_multispectral_bang)

# calculate ndvi with naip
naip_multispectral_bang[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bang <- (naip_multispectral_bang[[4]] - naip_multispectral_bang[[1]]) / (naip_multispectral_bang[[4]] + naip_multispectral_bang[[1]])

# plot the data
plot(naip_ndvi_bang,
     main = "NDVI of Bangkok, Thailand 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bang,
  main = "NDVI: Distribution of pixels\n NAIP Bangkok, Thailand  (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_bask <- stack("~/GreenSpace_Thesis/Google Earth Images/Basking Ridge, NJ 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bask <- brick(naip_multispectral_bask)

# calculate ndvi with naip
naip_multispectral_bask[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bask <- (naip_multispectral_bask[[4]] - naip_multispectral_bask[[1]]) / (naip_multispectral_bask[[4]] + naip_multispectral_bask[[1]])

# plot the data
plot(naip_ndvi_bask,
     main = "NDVI of Basking Ridge, NJ 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bask,
  main = "NDVI: Distribution of pixels\n NAIP Basking Ridge, NJ  (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_beij <- stack("~/GreenSpace_Thesis/Google Earth Images/Beijing, China 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_beij <- brick(naip_multispectral_beij)

# calculate ndvi with naip
naip_multispectral_beij[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_beij <- (naip_multispectral_beij[[4]] - naip_multispectral_beij[[1]]) / (naip_multispectral_beij[[4]] + naip_multispectral_beij[[1]])

# plot the data
plot(naip_ndvi_beij,
     main = "NDVI of Beijing, China 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_beij,
  main = "NDVI: Distribution of pixels\n NAIP Beijing, China  (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_bel <- stack("~/GreenSpace_Thesis/Google Earth Images/Bellflower, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bel <- brick(naip_multispectral_bel)

# calculate ndvi with naip
naip_multispectral_bel[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bel <- (naip_multispectral_bel[[4]] - naip_multispectral_bel[[1]]) / (naip_multispectral_bel[[4]] + naip_multispectral_bel[[1]])

# plot the data
plot(naip_ndvi_bel,
     main = "NDVI of Bellflower, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bel,
  main = "NDVI: Distribution of pixels\n NAIP Bellflower, CA  (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_belt <- stack("~/GreenSpace_Thesis/Google Earth Images/Bell Bethesda, MD 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_belt <- brick(naip_multispectral_belt)

# calculate ndvi with naip
naip_multispectral_belt[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_belt <- (naip_multispectral_belt[[4]] - naip_multispectral_belt[[1]]) / (naip_multispectral_belt[[4]] + naip_multispectral_belt[[1]])

# plot the data
plot(naip_ndvi_belt,
     main = "NDVI of Bell Bethesda, MD 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_belt,
  main = "NDVI: Distribution of pixels\n NAIP Bell Bethesda, MD  (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_bhp <- stack("~/GreenSpace_Thesis/Google Earth Images/Bhopal, India 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bhp <- brick(naip_multispectral_bhp)

# calculate ndvi with naip
naip_multispectral_bhp[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bhp <- (naip_multispectral_bhp[[4]] - naip_multispectral_bhp[[1]]) / (naip_multispectral_bhp[[4]] + naip_multispectral_bhp[[1]])

# plot the data
plot(naip_ndvi_bhp,
     main = "NDVI of Bhopal, India 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bhp,
  main = "NDVI: Distribution of pixels\n NAIP Bhopal, India (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_bou <- stack("~/GreenSpace_Thesis/Google Earth Images/Boulder, CO 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bou <- brick(naip_multispectral_bou)

# calculate ndvi with naip
naip_multispectral_bou[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bou <- (naip_multispectral_bou[[4]] - naip_multispectral_bou[[1]]) / (naip_multispectral_bou[[4]] + naip_multispectral_bou[[1]])

# plot the data
plot(naip_ndvi_bou,
     main = "NDVI of Boulder, CO 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bou,
  main = "NDVI: Distribution of pixels\n NAIP Boulder, CO (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_bre <- stack("~/GreenSpace_Thesis/Google Earth Images/Brea, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_bre <- brick(naip_multispectral_bre)

# calculate ndvi with naip
naip_multispectral_bre[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_bre <- (naip_multispectral_bre[[4]] - naip_multispectral_bre[[1]]) / (naip_multispectral_bre[[4]] + naip_multispectral_bre[[1]])

# plot the data
plot(naip_ndvi_bre,
     main = "NDVI of Brea, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_bou,
  main = "NDVI: Distribution of pixels\n NAIP Brea, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_carl <- stack("~/GreenSpace_Thesis/Google Earth Images/Carlsbad, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_carl <- brick(naip_multispectral_carl)

# calculate ndvi with naip
naip_multispectral_carl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_carl <- (naip_multispectral_carl[[4]] - naip_multispectral_carl[[1]]) / (naip_multispectral_carl[[4]] + naip_multispectral_carl[[1]])

# plot the data
plot(naip_ndvi_carl,
     main = "NDVI of Carlsbad, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_carl,
  main = "NDVI: Distribution of pixels\n NAIP Carlsbad, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_carm <- stack("~/GreenSpace_Thesis/Google Earth Images/Carmel Valley, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_carm <- brick(naip_multispectral_carm)

# calculate ndvi with naip
naip_multispectral_carm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_carm <- (naip_multispectral_carm[[4]] - naip_multispectral_carm[[1]]) / (naip_multispectral_carm[[4]] + naip_multispectral_carm[[1]])

# plot the data
plot(naip_ndvi_carm,
     main = "NDVI of Carmel Valley, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_carm,
  main = "NDVI: Distribution of pixels\n NAIP Carmel Valley, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_che <- stack("~/GreenSpace_Thesis/Google Earth Images/Chengdu, Suchuan, China 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_che <- brick(naip_multispectral_che)

# calculate ndvi with naip
naip_multispectral_che[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_che <- (naip_multispectral_che[[4]] - naip_multispectral_che[[1]]) / (naip_multispectral_che[[4]] + naip_multispectral_che[[1]])

# plot the data
plot(naip_ndvi_che,
     main = "NDVI of Chengdu, Suchuan, China 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_che,
  main = "NDVI: Distribution of pixels\n NAIP Chengdu, Suchuan, China (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_chi <- stack("~/GreenSpace_Thesis/Google Earth Images/Chino Hills, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_chi <- brick(naip_multispectral_chi)

# calculate ndvi with naip
naip_multispectral_chi[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_chi <- (naip_multispectral_chi[[4]] - naip_multispectral_chi[[1]]) / (naip_multispectral_chi[[4]] + naip_multispectral_chi[[1]])

# plot the data
plot(naip_ndvi_chi,
     main = "NDVI of Chino Hills, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_chi,
  main = "NDVI: Distribution of pixels\n NAIP Chino Hills, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_cho <- stack("~/GreenSpace_Thesis/Google Earth Images/Chongquing, China 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_cho <- brick(naip_multispectral_cho)

# calculate ndvi with naip
naip_multispectral_cho[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_cho <- (naip_multispectral_cho[[4]] - naip_multispectral_cho[[1]]) / (naip_multispectral_cho[[4]] + naip_multispectral_cho[[1]])

# plot the data
plot(naip_ndvi_cho,
     main = "NDVI of Chongquing, China 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_cho,
  main = "NDVI: Distribution of pixels\n NAIP Chongquing, China (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_cla <- stack("~/GreenSpace_Thesis/Google Earth Images/Clarksville, MD 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_cla <- brick(naip_multispectral_cla)

# calculate ndvi with naip
naip_multispectral_cla[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_cla <- (naip_multispectral_cla[[4]] - naip_multispectral_cla[[1]]) / (naip_multispectral_cla[[4]] + naip_multispectral_cla[[1]])

# plot the data
plot(naip_ndvi_cla,
     main = "NDVI of Clarksville, MD 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_cla,
  main = "NDVI: Distribution of pixels\n NAIP Clarksville, MD (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_cle <- stack("~/GreenSpace_Thesis/Google Earth Images/Clearlake, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_cle <- brick(naip_multispectral_cle)

# calculate ndvi with naip
naip_multispectral_cle[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_cle <- (naip_multispectral_cle[[4]] - naip_multispectral_cle[[1]]) / (naip_multispectral_cle[[4]] + naip_multispectral_cle[[1]])

# plot the data
plot(naip_ndvi_cle,
     main = "NDVI of Clearlake, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_cle,
  main = "NDVI: Distribution of pixels\n NAIP Clearlake, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_clew <- stack("~/GreenSpace_Thesis/Google Earth Images/Clearwater, FL 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_clew <- brick(naip_multispectral_clew)

# calculate ndvi with naip
naip_multispectral_clew[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_clew <- (naip_multispectral_clew[[4]] - naip_multispectral_clew[[1]]) / (naip_multispectral_clew[[4]] + naip_multispectral_clew[[1]])

# plot the data
plot(naip_ndvi_clew,
     main = "NDVI of Clearwater, FL 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_clew,
  main = "NDVI: Distribution of pixels\n NAIP Clearwater, FL (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_col <- stack("~/GreenSpace_Thesis/Google Earth Images/Colombo, Sri Lanka 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_col <- brick(naip_multispectral_col)

# calculate ndvi with naip
naip_multispectral_col[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_col <- (naip_multispectral_col[[4]] - naip_multispectral_col[[1]]) / (naip_multispectral_col[[4]] + naip_multispectral_col[[1]])

# plot the data
plot(naip_ndvi_col,
     main = "NDVI of Colombo, Sri Lanka 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_col,
  main = "NDVI: Distribution of pixels\n NAIP Colombo, Sri Lanka (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_colo <- stack("~/GreenSpace_Thesis/Google Earth Images/Colorado Springs, CO 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_colo <- brick(naip_multispectral_colo)

# calculate ndvi with naip
naip_multispectral_colo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_colo <- (naip_multispectral_colo[[4]] - naip_multispectral_colo[[1]]) / (naip_multispectral_colo[[4]] + naip_multispectral_colo[[1]])

# plot the data
plot(naip_ndvi_colo,
     main = "NDVI of Colorado Springs, CO 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_colo,
  main = "NDVI: Distribution of pixels\n NAIP Colorado Springs, CO (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_colum <- stack("~/GreenSpace_Thesis/Google Earth Images/Colombus, Ohio 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_colum <- brick(naip_multispectral_colum)

# calculate ndvi with naip
naip_multispectral_colum[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_colum <- (naip_multispectral_colum[[4]] - naip_multispectral_colum[[1]]) / (naip_multispectral_colum[[4]] + naip_multispectral_colum[[1]])

# plot the data
plot(naip_ndvi_colum,
     main = "NDVI of Colombus, Ohio 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_colum,
  main = "NDVI: Distribution of pixels\n NAIP Colombus, Ohio (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_con <- stack("~/GreenSpace_Thesis/Google Earth Images/Concord, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_con <- brick(naip_multispectral_con)

# calculate ndvi with naip
naip_multispectral_con[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_con <- (naip_multispectral_con[[4]] - naip_multispectral_con[[1]]) / (naip_multispectral_con[[4]] + naip_multispectral_con[[1]])

# plot the data
plot(naip_ndvi_con,
     main = "NDVI of Concord, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_con,
  main = "NDVI: Distribution of pixels\n NAIP Concord, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_con <- stack("~/GreenSpace_Thesis/Google Earth Images/Coronado, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_con <- brick(naip_multispectral_con)

# calculate ndvi with naip
naip_multispectral_con[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_con <- (naip_multispectral_con[[4]] - naip_multispectral_con[[1]]) / (naip_multispectral_con[[4]] + naip_multispectral_con[[1]])

# plot the data
plot(naip_ndvi_con,
     main = "NDVI of Coronado, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_con,
  main = "NDVI: Distribution of pixels\n NAIP Coronado, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_cort <- stack("~/GreenSpace_Thesis/Google Earth Images/Corte Madera, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_cort <- brick(naip_multispectral_cort)

# calculate ndvi with naip
naip_multispectral_cort[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_cort <- (naip_multispectral_cort[[4]] - naip_multispectral_cort[[1]]) / (naip_multispectral_cort[[4]] + naip_multispectral_cort[[1]])

# plot the data
plot(naip_ndvi_cort,
     main = "NDVI of Corte Madera, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_cort,
  main = "NDVI: Distribution of pixels\n NAIP Corte Madera, CA (1 mile radius)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_cup <- stack("~/GreenSpace_Thesis/Google Earth Images/Cupertino, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_cup <- brick(naip_multispectral_cup)

# calculate ndvi with naip
naip_multispectral_cup[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_cup <- (naip_multispectral_cup[[4]] - naip_multispectral_cup[[1]]) / (naip_multispectral_cup[[4]] + naip_multispectral_cup[[1]])

# plot the data
plot(naip_ndvi_cup,
     main = "NDVI of Cupertino, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_cup,
  main = "NDVI: Distribution of pixels\n NAIP Cupertino, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_dal <- stack("~/GreenSpace_Thesis/Google Earth Images/Daly City, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_dal <- brick(naip_multispectral_dal)

# calculate ndvi with naip
naip_multispectral_dal[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_dal <- (naip_multispectral_dal[[4]] - naip_multispectral_dal[[1]]) / (naip_multispectral_dal[[4]] + naip_multispectral_dal[[1]])

# plot the data
plot(naip_ndvi_dal,
     main = "NDVI of Daly City, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_dal,
  main = "NDVI: Distribution of pixels\n NAIP Daly City, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_dan <- stack("~/GreenSpace_Thesis/Google Earth Images/Danville, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_dan <- brick(naip_multispectral_dan)

# calculate ndvi with naip
naip_multispectral_dan[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_dan <- (naip_multispectral_dan[[4]] - naip_multispectral_dan[[1]]) / (naip_multispectral_dan[[4]] + naip_multispectral_dan[[1]])

# plot the data
plot(naip_ndvi_dan,
     main = "NDVI of Danville, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_dan,
  main = "NDVI: Distribution of pixels\n NAIP Danville, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_dav <- stack("~/GreenSpace_Thesis/Google Earth Images/Davis, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_dav <- brick(naip_multispectral_dav)

# calculate ndvi with naip
naip_multispectral_dav[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_dav <- (naip_multispectral_dav[[4]] - naip_multispectral_dav[[1]]) / (naip_multispectral_dav[[4]] + naip_multispectral_dav[[1]])

# plot the data
plot(naip_ndvi_dav,
     main = "NDVI of Davis, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_dav,
  main = "NDVI: Distribution of pixels\n NAIP Davis, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_del <- stack("~/GreenSpace_Thesis/Google Earth Images/Del Mar, CA 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_del <- brick(naip_multispectral_del)

# calculate ndvi with naip
naip_multispectral_del[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_del <- (naip_multispectral_del[[4]] - naip_multispectral_del[[1]]) / (naip_multispectral_del[[4]] + naip_multispectral_del[[1]])

# plot the data
plot(naip_ndvi_del,
     main = "NDVI of Del Mar, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_del,
  main = "NDVI: Distribution of pixels\n NAIP Del Mar, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_delm <- stack("~/GreenSpace_Thesis/Google Earth Images/Delmar, NY 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_delm <- brick(naip_multispectral_delm)

# calculate ndvi with naip
naip_multispectral_delm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_delm <- (naip_multispectral_delm[[4]] - naip_multispectral_delm[[1]]) / (naip_multispectral_delm[[4]] + naip_multispectral_delm[[1]])

# plot the data
plot(naip_ndvi_delm,
     main = "NDVI of Delmar, NY 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_delm,
  main = "NDVI: Distribution of pixels\n NAIP Delmar, NY (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_den <- stack("~/GreenSpace_Thesis/Google Earth Images/Denver, CO 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_den <- brick(naip_multispectral_den)

# calculate ndvi with naip
naip_multispectral_den[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_den <- (naip_multispectral_den[[4]] - naip_multispectral_den[[1]]) / (naip_multispectral_den[[4]] + naip_multispectral_den[[1]])

# plot the data
plot(naip_ndvi_den,
     main = "NDVI of Denver, CO 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_den,
  main = "NDVI: Distribution of pixels\n NAIP Denver, CO (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_det <- stack("~/GreenSpace_Thesis/Google Earth Images/Detroit, Michigan 1 mile.png")
# convert data into rasterbrick for faster processing

naip_multispectral_det <- brick(naip_multispectral_det)

# calculate ndvi with naip
naip_multispectral_det[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_det <- (naip_multispectral_det[[4]] - naip_multispectral_det[[1]]) / (naip_multispectral_det[[4]] + naip_multispectral_det[[1]])

# plot the data
plot(naip_ndvi_det,
     main = "NDVI of Detroit, Michigan 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_det,
  main = "NDVI: Distribution of pixels\n NAIP Detroit, Michigan (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_di <- stack("~/GreenSpace_Thesis/Google Earth Images/Diamond Bar, CA .png")
# convert data into rasterbrick for faster processing

naip_multispectral_di <- brick(naip_multispectral_di)

# calculate ndvi with naip
naip_multispectral_di[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_di <- (naip_multispectral_di[[4]] - naip_multispectral_di[[1]]) / (naip_multispectral_di[[4]] + naip_multispectral_di[[1]])

# plot the data
plot(naip_ndvi_di,
     main = "NDVI of Diamond Bar, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_di,
  main = "NDVI: Distribution of pixels\n NAIP Diamond Bar, CA (1 mile reference)",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_du <- stack("~/GreenSpace_Thesis/Google Earth Images/Dubai, United Arab Emirates.png")
# convert data into rasterbrick for faster processing

naip_multispectral_du <- brick(naip_multispectral_du)

# calculate ndvi with naip
naip_multispectral_du[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_du <- (naip_multispectral_du[[4]] - naip_multispectral_du[[1]]) / (naip_multispectral_du[[4]] + naip_multispectral_du[[1]])

# plot the data
plot(naip_ndvi_du,
     main = "NDVI of Dubai, United Arab Emirates 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_du,
  main = "NDVI: Distribution of pixels\n NAIP Dubai, United Arab Emirates",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_dub <- stack("~/GreenSpace_Thesis/Google Earth Images/Dublin, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_dub <- brick(naip_multispectral_dub)

# calculate ndvi with naip
naip_multispectral_dub[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_dub <- (naip_multispectral_dub[[4]] - naip_multispectral_dub[[1]]) / (naip_multispectral_dub[[4]] + naip_multispectral_dub[[1]])

# plot the data
plot(naip_ndvi_dub,
     main = "NDVI of Dublin, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_dub,
  main = "NDVI: Distribution of pixels\n NAIP Dublin, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ea <- stack("~/GreenSpace_Thesis/Google Earth Images/East Oakland, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ea <- brick(naip_multispectral_ea)

# calculate ndvi with naip
naip_multispectral_ea[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ea <- (naip_multispectral_ea[[4]] - naip_multispectral_ea[[1]]) / (naip_multispectral_ea[[4]] + naip_multispectral_ea[[1]])

# plot the data
plot(naip_ndvi_ea,
     main = "NDVI of East Oakland, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ea,
  main = "NDVI: Distribution of pixels\n NAIP East Oakland, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ed <- stack("~/GreenSpace_Thesis/Google Earth Images/Edgewater, NJ .png")
# convert data into rasterbrick for faster processing

naip_multispectral_ed <- brick(naip_multispectral_ed)

# calculate ndvi with naip
naip_multispectral_ed[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ed <- (naip_multispectral_ed[[4]] - naip_multispectral_ed[[1]]) / (naip_multispectral_ed[[4]] + naip_multispectral_ed[[1]])

# plot the data
plot(naip_ndvi_ed,
     main = "NDVI of Edgewater, NJ 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ed,
  main = "NDVI: Distribution of pixels\n NAIP Edgewater, NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_el <- stack("~/GreenSpace_Thesis/Google Earth Images/El Centro, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_el <- brick(naip_multispectral_el)

# calculate ndvi with naip
naip_multispectral_el[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_el <- (naip_multispectral_el[[4]] - naip_multispectral_el[[1]]) / (naip_multispectral_el[[4]] + naip_multispectral_el[[1]])

# plot the data
plot(naip_ndvi_el,
     main = "NDVI of El Centro, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_el,
  main = "NDVI: Distribution of pixels\n NAIP El Centro, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_elk <- stack("~/GreenSpace_Thesis/Google Earth Images/Elk Grove, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_elk <- brick(naip_multispectral_elk)

# calculate ndvi with naip
naip_multispectral_elk[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_elk <- (naip_multispectral_elk[[4]] - naip_multispectral_elk[[1]]) / (naip_multispectral_elk[[4]] + naip_multispectral_elk[[1]])

# plot the data
plot(naip_ndvi_elk,
     main = "NDVI of Elk Grove, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_elk,
  main = "NDVI: Distribution of pixels\n NAIP Elk Grove, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ell <- stack("~/GreenSpace_Thesis/Google Earth Images/Ellicott City, Maryland.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ell <- brick(naip_multispectral_ell)

# calculate ndvi with naip
naip_multispectral_ell[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ell <- (naip_multispectral_ell[[4]] - naip_multispectral_ell[[1]]) / (naip_multispectral_ell[[4]] + naip_multispectral_ell[[1]])

# plot the data
plot(naip_ndvi_ell,
     main = "NDVI of Ellicott City, Maryland 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ell,
  main = "NDVI: Distribution of pixels\n NAIP Ellicott City, Maryland",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_en <- stack("~/GreenSpace_Thesis/Google Earth Images/Encinitas, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_en <- brick(naip_multispectral_en)

# calculate ndvi with naip
naip_multispectral_en[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_en <- (naip_multispectral_en[[4]] - naip_multispectral_en[[1]]) / (naip_multispectral_en[[4]] + naip_multispectral_en[[1]])

# plot the data
plot(naip_ndvi_en,
     main = "NDVI of Encinitas, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_en,
  main = "NDVI: Distribution of pixels\n NAIP Encinitas, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_ens <- stack("~/GreenSpace_Thesis/Google Earth Images/Surrey, England.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ens <- brick(naip_multispectral_ens)

# calculate ndvi with naip
naip_multispectral_ens[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ens <- (naip_multispectral_ens[[4]] - naip_multispectral_ens[[1]]) / (naip_multispectral_ens[[4]] + naip_multispectral_ens[[1]])

# plot the data
plot(naip_ndvi_ens,
     main = "NDVI of Surrey, England 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ens,
  main = "NDVI: Distribution of pixels\n NAIP Surrey, England",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fo <- stack("~/GreenSpace_Thesis/Google Earth Images/Fair Oaks, CA .png")
# convert data into rasterbrick for faster processing

naip_multispectral_fo <- brick(naip_multispectral_fo)

# calculate ndvi with naip
naip_multispectral_fo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fo <- (naip_multispectral_fo[[4]] - naip_multispectral_fo[[1]]) / (naip_multispectral_fo[[4]] + naip_multispectral_fo[[1]])

# plot the data
plot(naip_ndvi_fo,
     main = "NDVI of Fair Oaks, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fo,
  main = "NDVI: Distribution of pixels\n NAIP Fair Oaks, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_fx <- stack("~/GreenSpace_Thesis/Google Earth Images/Fairfax, VA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fx <- brick(naip_multispectral_fx)

# calculate ndvi with naip
naip_multispectral_fx[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fx <- (naip_multispectral_fx[[4]] - naip_multispectral_fx[[1]]) / (naip_multispectral_fx[[4]] + naip_multispectral_fx[[1]])

# plot the data
plot(naip_ndvi_fx,
     main = "NDVI of Fairfax, VA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fx,
  main = "NDVI: Distribution of pixels\n NAIP Fairfax, VA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fa <- stack("~/GreenSpace_Thesis/Google Earth Images/Fairfeild, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fa <- brick(naip_multispectral_fa)

# calculate ndvi with naip
naip_multispectral_fa[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fa <- (naip_multispectral_fa[[4]] - naip_multispectral_fa[[1]]) / (naip_multispectral_fa[[4]] + naip_multispectral_fa[[1]])

# plot the data
plot(naip_ndvi_fa,
     main = "NDVI of Fairfield, CA 1 mile",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fa,
  main = "NDVI: Distribution of pixels\n NAIP Fairfeild, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fed <- stack("~/GreenSpace_Thesis/Google Earth Images/Federal Way, WA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fed <- brick(naip_multispectral_fed)

# calculate ndvi with naip
naip_multispectral_fed[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fed <- (naip_multispectral_fed[[4]] - naip_multispectral_fed[[1]]) / (naip_multispectral_fed[[4]] + naip_multispectral_fed[[1]])

# plot the data
plot(naip_ndvi_fed,
     main = "NDVI of Federal Way, WA ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fed,
  main = "NDVI: Distribution of pixels\n NAIP Federal Way, WA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fon <- stack("~/GreenSpace_Thesis/Google Earth Images/Fontana, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fon <- brick(naip_multispectral_fon)

# calculate ndvi with naip
naip_multispectral_fon[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fon <- (naip_multispectral_fon[[4]] - naip_multispectral_fon[[1]]) / (naip_multispectral_fon[[4]] + naip_multispectral_fon[[1]])

# plot the data
plot(naip_ndvi_fon,
     main = "NDVI of Fontana, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fon,
  main = "NDVI: Distribution of pixels\n NAIP Fontana, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_for <- stack("~/GreenSpace_Thesis/Google Earth Images/Fortuna, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_for <- brick(naip_multispectral_for)

# calculate ndvi with naip
naip_multispectral_for[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_for <- (naip_multispectral_for[[4]] - naip_multispectral_for[[1]]) / (naip_multispectral_for[[4]] + naip_multispectral_for[[1]])

# plot the data
plot(naip_ndvi_for,
     main = "NDVI of Fortuna, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_for,
  main = "NDVI: Distribution of pixels\n NAIP Fortuna, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fre <- stack("~/GreenSpace_Thesis/Google Earth Images/Freehold, NJ.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fre <- brick(naip_multispectral_fre)

# calculate ndvi with naip
naip_multispectral_fre[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fre <- (naip_multispectral_fre[[4]] - naip_multispectral_fre[[1]]) / (naip_multispectral_fre[[4]] + naip_multispectral_fre[[1]])

# plot the data
plot(naip_ndvi_fre,
     main = "NDVI of Freehold, NJ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fre,
  main = "NDVI: Distribution of pixels\n NAIP Freehold NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_frem <- stack("~/GreenSpace_Thesis/Google Earth Images/Fremont, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_frem <- brick(naip_multispectral_frem)

# calculate ndvi with naip
naip_multispectral_frem[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_frem <- (naip_multispectral_frem[[4]] - naip_multispectral_frem[[1]]) / (naip_multispectral_frem[[4]] + naip_multispectral_frem[[1]])

# plot the data
plot(naip_ndvi_frem,
     main = "NDVI of Fremont, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_frem,
  main = "NDVI: Distribution of pixels\n NAIP Fremont, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fres <- stack("~/GreenSpace_Thesis/Google Earth Images/Fresno, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fres <- brick(naip_multispectral_fres)

# calculate ndvi with naip
naip_multispectral_fres[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fres <- (naip_multispectral_fres[[4]] - naip_multispectral_fres[[1]]) / (naip_multispectral_fres[[4]] + naip_multispectral_fres[[1]])

# plot the data
plot(naip_ndvi_fres,
     main = "NDVI of Fresno, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fres,
  main = "NDVI: Distribution of pixels\n NAIP Fresno, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_fri <- stack("~/GreenSpace_Thesis/Google Earth Images/Frisco, TX.png")
# convert data into rasterbrick for faster processing

naip_multispectral_fri <- brick(naip_multispectral_fri)

# calculate ndvi with naip
naip_multispectral_fri[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_fri <- (naip_multispectral_fri[[4]] - naip_multispectral_fri[[1]]) / (naip_multispectral_fri[[4]] + naip_multispectral_fri[[1]])

# plot the data
plot(naip_ndvi_fri,
     main = "NDVI of Frisco, TX",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_fri,
  main = "NDVI: Distribution of pixels\n NAIP Frisco, TX",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ful <- stack("~/GreenSpace_Thesis/Google Earth Images/Fullerton, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ful <- brick(naip_multispectral_ful)

# calculate ndvi with naip
naip_multispectral_ful[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ful <- (naip_multispectral_ful[[4]] - naip_multispectral_ful[[1]]) / (naip_multispectral_ful[[4]] + naip_multispectral_ful[[1]])

# plot the data
plot(naip_ndvi_ful,
     main = "NDVI of Fullerton, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ful,
  main = "NDVI: Distribution of pixels\n NAIP Fullerton, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ga <- stack("~/GreenSpace_Thesis/Google Earth Images/Gangnam-gu, Seoul, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ga <- brick(naip_multispectral_ga)

# calculate ndvi with naip
naip_multispectral_ga[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ga <- (naip_multispectral_ga[[4]] - naip_multispectral_ga[[1]]) / (naip_multispectral_ga[[4]] + naip_multispectral_ga[[1]])

# plot the data
plot(naip_ndvi_ga,
     main = "NDVI of Gangnam-gu, Seoul, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ga,
  main = "NDVI: Distribution of pixels\n NAIP Gangnam-gu, Seoul, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_gay <- stack("~/GreenSpace_Thesis/Google Earth Images/Gayang-dong, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_gay <- brick(naip_multispectral_gay)

# calculate ndvi with naip
naip_multispectral_gay[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_gay <- (naip_multispectral_gay[[4]] - naip_multispectral_gay[[1]]) / (naip_multispectral_gay[[4]] + naip_multispectral_gay[[1]])

# plot the data
plot(naip_ndvi_gay,
     main = "NDVI of Gayang-dong, Seoul, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_gay,
  main = "NDVI: Distribution of pixels\n NAIP Gayang-dong, Seoul, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ge <- stack("~/GreenSpace_Thesis/Google Earth Images/Geumjeong-gu, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ge <- brick(naip_multispectral_ge)

# calculate ndvi with naip
naip_multispectral_ge[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ge <- (naip_multispectral_ge[[4]] - naip_multispectral_ge[[1]]) / (naip_multispectral_ge[[4]] + naip_multispectral_ge[[1]])

# plot the data
plot(naip_ndvi_ge,
     main = "NDVI of GeumJeong-gu, Busan, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ge,
  main = "NDVI: Distribution of pixels\n NAIP GeumJeong-gu, Busan, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_gl <- stack("~/GreenSpace_Thesis/Google Earth Images/Glendale, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_gl <- brick(naip_multispectral_gl)

# calculate ndvi with naip
naip_multispectral_gl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_gl <- (naip_multispectral_gl[[4]] - naip_multispectral_gl[[1]]) / (naip_multispectral_gl[[4]] + naip_multispectral_gl[[1]])

# plot the data
plot(naip_ndvi_gl,
     main = "NDVI of Glendale, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_gl,
  main = "NDVI: Distribution of pixels\n NAIP Glendale, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_gr <- stack("~/GreenSpace_Thesis/Google Earth Images/Grass Valley, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_gr <- brick(naip_multispectral_gr)

# calculate ndvi with naip
naip_multispectral_gr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_gr <- (naip_multispectral_gr[[4]] - naip_multispectral_gr[[1]]) / (naip_multispectral_gr[[4]] + naip_multispectral_gr[[1]])

# plot the data
plot(naip_ndvi_gr,
     main = "NDVI of Grass Valley, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_gr,
  main = "NDVI: Distribution of pixels\n NAIP Grass Valley, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_gre <- stack("~/GreenSpace_Thesis/Google Earth Images/Greenfield, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_gre <- brick(naip_multispectral_gre)

# calculate ndvi with naip
naip_multispectral_gre[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_gre <- (naip_multispectral_gre[[4]] - naip_multispectral_gre[[1]]) / (naip_multispectral_gre[[4]] + naip_multispectral_gre[[1]])

# plot the data
plot(naip_ndvi_gre,
     main = "NDVI of Greenfield, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_gre,
  main = "NDVI: Distribution of pixels\n NAIP Greenfield, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_gu <- stack("~/GreenSpace_Thesis/Google Earth Images/Gurugram, India.png")
# convert data into rasterbrick for faster processing

naip_multispectral_gu <- brick(naip_multispectral_gu)

# calculate ndvi with naip
naip_multispectral_gu[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_gu <- (naip_multispectral_gu[[4]] - naip_multispectral_gu[[1]]) / (naip_multispectral_gu[[4]] + naip_multispectral_gu[[1]])

# plot the data
plot(naip_ndvi_gu,
     main = "NDVI of Gurgaon, Haryana, India",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_gu,
  main = "NDVI: Distribution of pixels\n NAIP Gurgaon, Haryana, India",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_hai <- stack("~/GreenSpace_Thesis/Google Earth Images/Haidian, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hai <- brick(naip_multispectral_hai)

# calculate ndvi with naip
naip_multispectral_hai[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hai <- (naip_multispectral_hai[[4]] - naip_multispectral_hai[[1]]) / (naip_multispectral_hai[[4]] + naip_multispectral_hai[[1]])

# plot the data
plot(naip_ndvi_hai,
     main = "NDVI of Haidian, Beijing, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hai,
  main = "NDVI: Distribution of pixels\n NAIP Haidian, Beijing, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_han <- stack("~/GreenSpace_Thesis/Google Earth Images/Hanford, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_han <- brick(naip_multispectral_han)

# calculate ndvi with naip
naip_multispectral_han[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_han <- (naip_multispectral_han[[4]] - naip_multispectral_han[[1]]) / (naip_multispectral_han[[4]] + naip_multispectral_han[[1]])

# plot the data
plot(naip_ndvi_han,
     main = "NDVI of Hanford, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_han,
  main = "NDVI: Distribution of pixels\n NAIP Hanford, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_ha <- stack("~/GreenSpace_Thesis/Google Earth Images/Hanoi, Vietnam.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ha <- brick(naip_multispectral_ha)

# calculate ndvi with naip
naip_multispectral_ha[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ha <- (naip_multispectral_ha[[4]] - naip_multispectral_ha[[1]]) / (naip_multispectral_ha[[4]] + naip_multispectral_ha[[1]])

# plot the data
plot(naip_ndvi_ha,
     main = "NDVI of Hanoi, Vietnam",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ha,
  main = "NDVI: Distribution of pixels\n NAIP Hanoi, Vietnam",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_haw <- stack("~/GreenSpace_Thesis/Google Earth Images/Hawthorne, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_haw <- brick(naip_multispectral_haw)

# calculate ndvi with naip
naip_multispectral_haw[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_haw <- (naip_multispectral_haw[[4]] - naip_multispectral_haw[[1]]) / (naip_multispectral_haw[[4]] + naip_multispectral_haw[[1]])

# plot the data
plot(naip_ndvi_haw,
     main = "NDVI of Hawthorne, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_haw,
  main = "NDVI: Distribution of pixels\n NAIP Hawthorne, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_hay <- stack("~/GreenSpace_Thesis/Google Earth Images/Hayward, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hay <- brick(naip_multispectral_hay)

# calculate ndvi with naip
naip_multispectral_hay[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hay <- (naip_multispectral_hay[[4]] - naip_multispectral_hay[[1]]) / (naip_multispectral_hay[[4]] + naip_multispectral_hay[[1]])

# plot the data
plot(naip_ndvi_hay,
     main = "NDVI of Hayward, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hay,
  main = "NDVI: Distribution of pixels\n NAIP Hayward, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_he <- stack("~/GreenSpace_Thesis/Google Earth Images/Hercules, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_he <- brick(naip_multispectral_he)

# calculate ndvi with naip
naip_multispectral_he[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_he <- (naip_multispectral_he[[4]] - naip_multispectral_he[[1]]) / (naip_multispectral_he[[4]] + naip_multispectral_he[[1]])

# plot the data
plot(naip_ndvi_he,
     main = "NDVI of Hercules, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_he,
  main = "NDVI: Distribution of pixels\n NAIP Hercules, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_her <- stack("~/GreenSpace_Thesis/Google Earth Images/Hermosa Beach, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_her <- brick(naip_multispectral_her)

# calculate ndvi with naip
naip_multispectral_her[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_her <- (naip_multispectral_her[[4]] - naip_multispectral_her[[1]]) / (naip_multispectral_her[[4]] + naip_multispectral_her[[1]])

# plot the data
plot(naip_ndvi_her,
     main = "NDVI of Hermosa Beach, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_her,
  main = "NDVI: Distribution of pixels\n NAIP Hermosa Beach, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```
```{r}
# import the naip pre-fire data
naip_multispectral_hern <- stack("~/GreenSpace_Thesis/Google Earth Images/Herndon, VA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hern <- brick(naip_multispectral_hern)

# calculate ndvi with naip
naip_multispectral_hern[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hern <- (naip_multispectral_hern[[4]] - naip_multispectral_hern[[1]]) / (naip_multispectral_hern[[4]] + naip_multispectral_hern[[1]])

# plot the data
plot(naip_ndvi_hern,
     main = "NDVI of Herndon, VA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hern,
  main = "NDVI: Distribution of pixels\n NAIP Herndon, VA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hi <- stack("~/GreenSpace_Thesis/Google Earth Images/Hillsborough, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hi <- brick(naip_multispectral_hi)

# calculate ndvi with naip
naip_multispectral_hi[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hi <- (naip_multispectral_hi[[4]] - naip_multispectral_hi[[1]]) / (naip_multispectral_hi[[4]] + naip_multispectral_hi[[1]])

# plot the data
plot(naip_ndvi_hi,
     main = "NDVI of Hillsborough, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hi,
  main = "NDVI: Distribution of pixels\n NAIP Hillsborough, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ho <- stack("~/GreenSpace_Thesis/Google Earth Images/Hong Kong.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ho <- brick(naip_multispectral_ho)

# calculate ndvi with naip
naip_multispectral_ho[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ho <- (naip_multispectral_ho[[4]] - naip_multispectral_ho[[1]]) / (naip_multispectral_ho[[4]] + naip_multispectral_ho[[1]])

# plot the data
plot(naip_ndvi_ho,
     main = "NDVI of Hong Kong",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ho,
  main = "NDVI: Distribution of pixels\n NAIP Hong Kong",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hon <- stack("~/GreenSpace_Thesis/Google Earth Images/Hongkou, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hon <- brick(naip_multispectral_hon)

# calculate ndvi with naip
naip_multispectral_hon[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hon <- (naip_multispectral_hon[[4]] - naip_multispectral_hon[[1]]) / (naip_multispectral_hon[[4]] + naip_multispectral_hon[[1]])

# plot the data
plot(naip_ndvi_hon,
     main = "NDVI of Hongkou, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hon,
  main = "NDVI: Distribution of pixels\n NAIP Hongkou, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hu <- stack("~/GreenSpace_Thesis/Google Earth Images/Hunan, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hu <- brick(naip_multispectral_hu)

# calculate ndvi with naip
naip_multispectral_hu[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hu <- (naip_multispectral_hu[[4]] - naip_multispectral_hu[[1]]) / (naip_multispectral_hu[[4]] + naip_multispectral_hu[[1]])

# plot the data
plot(naip_ndvi_hu,
     main = "NDVI of Hunan, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hu,
  main = "NDVI: Distribution of pixels\n NAIP Hunan, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hun <- stack("~/GreenSpace_Thesis/Google Earth Images/Hung Hom, Hong Kong.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hun <- brick(naip_multispectral_hun)

# calculate ndvi with naip
naip_multispectral_hun[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hun <- (naip_multispectral_hun[[4]] - naip_multispectral_hun[[1]]) / (naip_multispectral_hun[[4]] + naip_multispectral_hun[[1]])

# plot the data
plot(naip_ndvi_hun,
     main = "NDVI of Hung Hom, Hong Kong",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hun,
  main = "NDVI: Distribution of pixels\n NAIP Hung Hom, Hong Kong",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hunt <- stack("~/GreenSpace_Thesis/Google Earth Images/Huntington Beach, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hunt <- brick(naip_multispectral_hunt)

# calculate ndvi with naip
naip_multispectral_hunt[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hunt <- (naip_multispectral_hunt[[4]] - naip_multispectral_hunt[[1]]) / (naip_multispectral_hunt[[4]] + naip_multispectral_hunt[[1]])

# plot the data
plot(naip_ndvi_hunt,
     main = "NDVI of Huntington Beach, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hunt,
  main = "NDVI: Distribution of pixels\n NAIP Huntington Beach, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_hunts <- stack("~/GreenSpace_Thesis/Google Earth Images/Huntington Station, NY.png")
# convert data into rasterbrick for faster processing

naip_multispectral_hunts <- brick(naip_multispectral_hunts)

# calculate ndvi with naip
naip_multispectral_hunts[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_hunts <- (naip_multispectral_hunts[[4]] - naip_multispectral_hunts[[1]]) / (naip_multispectral_hunts[[4]] + naip_multispectral_hunts[[1]])

# plot the data
plot(naip_ndvi_hunts,
     main = "NDVI of Huntington Station, NY",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_hunts,
  main = "NDVI: Distribution of pixels\n NAIP Huntington Station, NY",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mo <- stack("~/GreenSpace_Thesis/Google Earth Images/Morelia, Mexico.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mo <- brick(naip_multispectral_mo)

# calculate ndvi with naip
naip_multispectral_mo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mo <- (naip_multispectral_mo[[4]] - naip_multispectral_mo[[1]]) / (naip_multispectral_mo[[4]] + naip_multispectral_mo[[1]])

# plot the data
plot(naip_ndvi_mo,
     main = "NDVI of Morelia, Mexico",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mo,
  main = "NDVI: Distribution of pixels\n NAIP Morelia, Mexico",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_st <- stack("~/GreenSpace_Thesis/Google Earth Images/Stockholm, Sweden.png")
# convert data into rasterbrick for faster processing

naip_multispectral_st <- brick(naip_multispectral_st)

# calculate ndvi with naip
naip_multispectral_st[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_st <- (naip_multispectral_st[[4]] - naip_multispectral_st[[1]]) / (naip_multispectral_st[[4]] + naip_multispectral_st[[1]])

# plot the data
plot(naip_ndvi_st,
     main = "NDVI of Stockholm, Sweden",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_st,
  main = "NDVI: Distribution of pixels\n NAIP Stockholm, Sweden",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_im <- stack("~/GreenSpace_Thesis/Google Earth Images/Imperial Beach, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_im <- brick(naip_multispectral_im)

# calculate ndvi with naip
naip_multispectral_im[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_im <- (naip_multispectral_im[[4]] - naip_multispectral_im[[1]]) / (naip_multispectral_im[[4]] + naip_multispectral_im[[1]])

# plot the data
plot(naip_ndvi_im,
     main = "NDVI of Imperial Beach, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_im,
  main = "NDVI: Distribution of pixels\n NAIP Imperial Beach, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ir <- stack("~/GreenSpace_Thesis/Google Earth Images/Irvine, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ir <- brick(naip_multispectral_ir)

# calculate ndvi with naip
naip_multispectral_ir[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ir <- (naip_multispectral_ir[[4]] - naip_multispectral_ir[[1]]) / (naip_multispectral_ir[[4]] + naip_multispectral_ir[[1]])

# plot the data
plot(naip_ndvi_ir,
     main = "NDVI of Irvine, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ir,
  main = "NDVI: Distribution of pixels\n NAIP Irvine, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_je <- stack("~/GreenSpace_Thesis/Google Earth Images/Jeju, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_je <- brick(naip_multispectral_je)

# calculate ndvi with naip
naip_multispectral_je[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_je <- (naip_multispectral_je[[4]] - naip_multispectral_je[[1]]) / (naip_multispectral_je[[4]] + naip_multispectral_je[[1]])

# plot the data
plot(naip_ndvi_je,
     main = "NDVI of Jeju, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_je,
  main = "NDVI: Distribution of pixels\n NAIP Jeju, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ji <- stack("~/GreenSpace_Thesis/Google Earth Images/Jiaozuo, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ji <- brick(naip_multispectral_ji)

# calculate ndvi with naip
naip_multispectral_ji[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ji <- (naip_multispectral_ji[[4]] - naip_multispectral_ji[[1]]) / (naip_multispectral_ji[[4]] + naip_multispectral_ji[[1]])

# plot the data
plot(naip_ndvi_ji,
     main = "NDVI of Jiaozuo, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ji,
  main = "NDVI: Distribution of pixels\n NAIP Jiaozuo, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_kai <- stack("~/GreenSpace_Thesis/Google Earth Images/Kai Ping, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_kai <- brick(naip_multispectral_kai)

# calculate ndvi with naip
naip_multispectral_kai[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_kai <- (naip_multispectral_kai[[4]] - naip_multispectral_kai[[1]]) / (naip_multispectral_kai[[4]] + naip_multispectral_kai[[1]])

# plot the data
plot(naip_ndvi_kai,
     main = "NDVI of Kai Ping, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_kai,
  main = "NDVI: Distribution of pixels\n NAIP Kai Ping, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_kat <- stack("~/GreenSpace_Thesis/Google Earth Images/Katy, TX.png")
# convert data into rasterbrick for faster processing

naip_multispectral_kat <- brick(naip_multispectral_kat)

# calculate ndvi with naip
naip_multispectral_kat[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_kat <- (naip_multispectral_kat[[4]] - naip_multispectral_kat[[1]]) / (naip_multispectral_kat[[4]] + naip_multispectral_kat[[1]])

# plot the data
plot(naip_ndvi_kat,
     main = "NDVI of Katy, TX",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_kat,
  main = "NDVI: Distribution of pixels\n NAIP Katy, TX",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ki <- stack("~/GreenSpace_Thesis/Google Earth Images/Kihei, HI.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ki <- brick(naip_multispectral_ki)

# calculate ndvi with naip
naip_multispectral_ki[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ki <- (naip_multispectral_ki[[4]] - naip_multispectral_ki[[1]]) / (naip_multispectral_ki[[4]] + naip_multispectral_ki[[1]])

# plot the data
plot(naip_ndvi_ki,
     main = "NDVI of Kihei, HI",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ki,
  main = "NDVI: Distribution of pixels\n NAIP Kihei, HI",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_kla <- stack("~/GreenSpace_Thesis/Google Earth Images/Klamath Falls, OR.png")
# convert data into rasterbrick for faster processing

naip_multispectral_kla <- brick(naip_multispectral_kla)

# calculate ndvi with naip
naip_multispectral_kla[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_kla <- (naip_multispectral_kla[[4]] - naip_multispectral_kla[[1]]) / (naip_multispectral_kla[[4]] + naip_multispectral_kla[[1]])

# plot the data
plot(naip_ndvi_kla,
     main = "NDVI of Klamath Falls, OR",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_kla,
  main = "NDVI: Distribution of pixels\n NAIP Klamath Falls, OR",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_la <- stack("~/GreenSpace_Thesis/Google Earth Images/La Canada, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_la <- brick(naip_multispectral_la)

# calculate ndvi with naip
naip_multispectral_la[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_la <- (naip_multispectral_la[[4]] - naip_multispectral_la[[1]]) / (naip_multispectral_la[[4]] + naip_multispectral_la[[1]])

# plot the data
plot(naip_ndvi_la,
     main = "NDVI of La Caada, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_la,
  main = "NDVI: Distribution of pixels\n NAIP La Caada, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_laf <- stack("~/GreenSpace_Thesis/Google Earth Images/Lafayette, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_laf <- brick(naip_multispectral_laf)

# calculate ndvi with naip
naip_multispectral_laf[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_laf <- (naip_multispectral_laf[[4]] - naip_multispectral_laf[[1]]) / (naip_multispectral_laf[[4]] + naip_multispectral_laf[[1]])

# plot the data
plot(naip_ndvi_laf,
     main = "NDVI of Lafayette, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_laf,
  main = "NDVI: Distribution of pixels\n NAIP Lafayette, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_lak <- stack("~/GreenSpace_Thesis/Google Earth Images/Lake Forest, WA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lak <- brick(naip_multispectral_lak)

# calculate ndvi with naip
naip_multispectral_lak[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lak <- (naip_multispectral_lak[[4]] - naip_multispectral_lak[[1]]) / (naip_multispectral_lak[[4]] + naip_multispectral_lak[[1]])

# plot the data
plot(naip_ndvi_lak,
     main = "NDVI of Lake Forest, WA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lak,
  main = "NDVI: Distribution of pixels\n NAIP Lake Forest, WA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lakw <- stack("~/GreenSpace_Thesis/Google Earth Images/Lakewood, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lakw <- brick(naip_multispectral_lakw)

# calculate ndvi with naip
naip_multispectral_lakw[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lakw <- (naip_multispectral_lakw[[4]] - naip_multispectral_lakw[[1]]) / (naip_multispectral_lakw[[4]] + naip_multispectral_lakw[[1]])

# plot the data
plot(naip_ndvi_lakw,
     main = "NDVI of Lakewood, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lakw,
  main = "NDVI: Distribution of pixels\n NAIP Lakewood, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lav <- stack("~/GreenSpace_Thesis/Google Earth Images/Las Vegas, NV.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lav <- brick(naip_multispectral_lav)

# calculate ndvi with naip
naip_multispectral_lav[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lav <- (naip_multispectral_lav[[4]] - naip_multispectral_lav[[1]]) / (naip_multispectral_lav[[4]] + naip_multispectral_lav[[1]])

# plot the data
plot(naip_ndvi_lav,
     main = "NDVI of Las Vegas, NV",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lav,
  main = "NDVI: Distribution of pixels\n NAIP Las Vegas, NV",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_li <- stack("~/GreenSpace_Thesis/Google Earth Images/Liaoning, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_li <- brick(naip_multispectral_li)

# calculate ndvi with naip
naip_multispectral_li[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_li <- (naip_multispectral_li[[4]] - naip_multispectral_li[[1]]) / (naip_multispectral_li[[4]] + naip_multispectral_li[[1]])

# plot the data
plot(naip_ndvi_li,
     main = "NDVI of Liaoning, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_li,
  main = "NDVI: Distribution of pixels\n NAIP Liaoning, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lib <- stack("~/GreenSpace_Thesis/Google Earth Images/Libertyville, IL.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lib <- brick(naip_multispectral_lib)

# calculate ndvi with naip
naip_multispectral_lib[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lib <- (naip_multispectral_lib[[4]] - naip_multispectral_lib[[1]]) / (naip_multispectral_lib[[4]] + naip_multispectral_lib[[1]])

# plot the data
plot(naip_ndvi_lib,
     main = "NDVI of Libertyville, IL",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lib,
  main = "NDVI: Distribution of pixels\n NAIP Libertyville, IL",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_liu <- stack("~/GreenSpace_Thesis/Google Earth Images/Liuzhou, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_liu <- brick(naip_multispectral_liu)

# calculate ndvi with naip
naip_multispectral_liu[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_liu <- (naip_multispectral_liu[[4]] - naip_multispectral_liu[[1]]) / (naip_multispectral_liu[[4]] + naip_multispectral_liu[[1]])

# plot the data
plot(naip_ndvi_liu,
     main = "NDVI of Liuzhou, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_liu,
  main = "NDVI: Distribution of pixels\n NAIP Liuzhou, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_liv <- stack("~/GreenSpace_Thesis/Google Earth Images/Livingston, NJ.png")
# convert data into rasterbrick for faster processing

naip_multispectral_liv <- brick(naip_multispectral_liv)

# calculate ndvi with naip
naip_multispectral_liv[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_liv <- (naip_multispectral_liv[[4]] - naip_multispectral_liv[[1]]) / (naip_multispectral_liv[[4]] + naip_multispectral_liv[[1]])

# plot the data
plot(naip_ndvi_liv,
     main = "NDVI of Livingston, NJ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_liv,
  main = "NDVI: Distribution of pixels\n NAIP Livingston, NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lo <- stack("~/GreenSpace_Thesis/Google Earth Images/Lompoc, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lo <- brick(naip_multispectral_lo)

# calculate ndvi with naip
naip_multispectral_lo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lo <- (naip_multispectral_lo[[4]] - naip_multispectral_lo[[1]]) / (naip_multispectral_lo[[4]] + naip_multispectral_lo[[1]])

# plot the data
plot(naip_ndvi_lo,
     main = "NDVI of Lompoc, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lo,
  main = "NDVI: Distribution of pixels\n NAIP Lompoc, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lon <- stack("~/GreenSpace_Thesis/Google Earth Images/Long Beach, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lon <- brick(naip_multispectral_lon)

# calculate ndvi with naip
naip_multispectral_lon[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lon <- (naip_multispectral_lon[[4]] - naip_multispectral_lon[[1]]) / (naip_multispectral_lon[[4]] + naip_multispectral_lon[[1]])

# plot the data
plot(naip_ndvi_lon,
     main = "NDVI of Long Beach, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lon,
  main = "NDVI: Distribution of pixels\n NAIP Long Beach, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_los <- stack("~/GreenSpace_Thesis/Google Earth Images/Los Altos, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_los <- brick(naip_multispectral_los)

# calculate ndvi with naip
naip_multispectral_los[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_los <- (naip_multispectral_los[[4]] - naip_multispectral_los[[1]]) / (naip_multispectral_los[[4]] + naip_multispectral_los[[1]])

# plot the data
plot(naip_ndvi_los,
     main = "NDVI of Los Altos, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_los,
  main = "NDVI: Distribution of pixels\n NAIP Los Altos, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_LA <- stack("~/GreenSpace_Thesis/Google Earth Images/Los Angeles, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_LA <- brick(naip_multispectral_LA)

# calculate ndvi with naip
naip_multispectral_LA[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_LA <- (naip_multispectral_LA[[4]] - naip_multispectral_LA[[1]]) / (naip_multispectral_LA[[4]] + naip_multispectral_LA[[1]])

# plot the data
plot(naip_ndvi_LA,
     main = "NDVI of Los Angeles, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_LA,
  main = "NDVI: Distribution of pixels\n NAIP Los Angeles, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_log <- stack("~/GreenSpace_Thesis/Google Earth Images/Los Gatos, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_log <- brick(naip_multispectral_log)

# calculate ndvi with naip
naip_multispectral_log[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_log <- (naip_multispectral_log[[4]] - naip_multispectral_log[[1]]) / (naip_multispectral_log[[4]] + naip_multispectral_log[[1]])

# plot the data
plot(naip_ndvi_log,
     main = "NDVI of Los Gatos, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_log,
  main = "NDVI: Distribution of pixels\n NAIP Los Gatos, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_lub <- stack("~/GreenSpace_Thesis/Google Earth Images/Lubbock, TX.png")
# convert data into rasterbrick for faster processing

naip_multispectral_lub <- brick(naip_multispectral_lub)

# calculate ndvi with naip
naip_multispectral_lub[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_lub <- (naip_multispectral_lub[[4]] - naip_multispectral_lub[[1]]) / (naip_multispectral_lub[[4]] + naip_multispectral_lub[[1]])

# plot the data
plot(naip_ndvi_lub,
     main = "NDVI of Lubbock, TX",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_lub,
  main = "NDVI: Distribution of pixels\n NAIP Lubbock, TX",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ma <- stack("~/GreenSpace_Thesis/Google Earth Images/Makati, Manila, Philippines.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ma <- brick(naip_multispectral_ma)

# calculate ndvi with naip
naip_multispectral_ma[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ma <- (naip_multispectral_ma[[4]] - naip_multispectral_ma[[1]]) / (naip_multispectral_ma[[4]] + naip_multispectral_ma[[1]])

# plot the data
plot(naip_ndvi_ma,
     main = "NDVI of Makati, Manila, Philippines",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ma,
  main = "NDVI: Distribution of pixels\n NAIP Makati, Manila, Philippines",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mar <- stack("~/GreenSpace_Thesis/Google Earth Images/Marin County, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mar <- brick(naip_multispectral_mar)

# calculate ndvi with naip
naip_multispectral_mar[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mar <- (naip_multispectral_mar[[4]] - naip_multispectral_mar[[1]]) / (naip_multispectral_mar[[4]] + naip_multispectral_mar[[1]])

# plot the data
plot(naip_ndvi_mar,
     main = "NDVI of Marin County, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mar,
  main = "NDVI: Distribution of pixels\n NAIP Marin County, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_med <- stack("~/GreenSpace_Thesis/Google Earth Images/Medina, WA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_med <- brick(naip_multispectral_med)

# calculate ndvi with naip
naip_multispectral_med[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_med <- (naip_multispectral_med[[4]] - naip_multispectral_med[[1]]) / (naip_multispectral_med[[4]] + naip_multispectral_med[[1]])

# plot the data
plot(naip_ndvi_med,
     main = "NDVI of Medina, WA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_med,
  main = "NDVI: Distribution of pixels\n NAIP Medina, WA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_men <- stack("~/GreenSpace_Thesis/Google Earth Images/Menlo, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_men <- brick(naip_multispectral_men)

# calculate ndvi with naip
naip_multispectral_men[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_men <- (naip_multispectral_men[[4]] - naip_multispectral_men[[1]]) / (naip_multispectral_men[[4]] + naip_multispectral_men[[1]])

# plot the data
plot(naip_ndvi_men,
     main = "NDVI of Menlo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_men,
  main = "NDVI: Distribution of pixels\n NAIP Menlo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mer <- stack("~/GreenSpace_Thesis/Google Earth Images/Merced, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mer <- brick(naip_multispectral_mer)

# calculate ndvi with naip
naip_multispectral_mer[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mer <- (naip_multispectral_mer[[4]] - naip_multispectral_mer[[1]]) / (naip_multispectral_mer[[4]] + naip_multispectral_mer[[1]])

# plot the data
plot(naip_ndvi_mer,
     main = "NDVI of Merced, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mer,
  main = "NDVI: Distribution of pixels\n NAIP Merced, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mi <- stack("~/GreenSpace_Thesis/Google Earth Images/Milpitas, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mi <- brick(naip_multispectral_mi)

# calculate ndvi with naip
naip_multispectral_mi[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mi <- (naip_multispectral_mi[[4]] - naip_multispectral_mi[[1]]) / (naip_multispectral_mi[[4]] + naip_multispectral_mi[[1]])

# plot the data
plot(naip_ndvi_mi,
     main = "NDVI of Milpitas, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mi,
  main = "NDVI: Distribution of pixels\n NAIP Milpitas, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_min <- stack("~/GreenSpace_Thesis/Google Earth Images/Minato, Japan.png")
# convert data into rasterbrick for faster processing

naip_multispectral_min <- brick(naip_multispectral_min)

# calculate ndvi with naip
naip_multispectral_min[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_min <- (naip_multispectral_min[[4]] - naip_multispectral_min[[1]]) / (naip_multispectral_min[[4]] + naip_multispectral_min[[1]])

# plot the data
plot(naip_ndvi_min,
     main = "NDVI of Minato, Japan",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_min,
  main = "NDVI: Distribution of pixels\n NAIP Minato, Japan",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mis <- stack("~/GreenSpace_Thesis/Google Earth Images/Mississauga, Ontario.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mis <- brick(naip_multispectral_mis)

# calculate ndvi with naip
naip_multispectral_mis[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mis <- (naip_multispectral_mis[[4]] - naip_multispectral_mis[[1]]) / (naip_multispectral_mis[[4]] + naip_multispectral_mis[[1]])

# plot the data
plot(naip_ndvi_mis,
     main = "NDVI of Mississauga, Ontario",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mis,
  main = "NDVI: Distribution of pixels\n NAIP Mississauga, Ontario",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_miz <- stack("~/GreenSpace_Thesis/Google Earth Images/Mizhuo, Japan.png")
# convert data into rasterbrick for faster processing

naip_multispectral_miz <- brick(naip_multispectral_miz)

# calculate ndvi with naip
naip_multispectral_miz[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_miz <- (naip_multispectral_miz[[4]] - naip_multispectral_miz[[1]]) / (naip_multispectral_miz[[4]] + naip_multispectral_miz[[1]])

# plot the data
plot(naip_ndvi_miz,
     main = "NDVI of Mizhuo, Japan",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_miz,
  main = "NDVI: Distribution of pixels\n NAIP Mizhuo, Japan",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mok <- stack("~/GreenSpace_Thesis/Google Earth Images/Mok-dong, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mok <- brick(naip_multispectral_mok)

# calculate ndvi with naip
naip_multispectral_mok[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mok <- (naip_multispectral_mok[[4]] - naip_multispectral_mok[[1]]) / (naip_multispectral_mok[[4]] + naip_multispectral_mok[[1]])

# plot the data
plot(naip_ndvi_mok,
     main = "NDVI of Mok-dong, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mok,
  main = "NDVI: Distribution of pixels\n NAIP Mok-dong, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mon <- stack("~/GreenSpace_Thesis/Google Earth Images/Monrovia, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mon <- brick(naip_multispectral_mon)

# calculate ndvi with naip
naip_multispectral_mon[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mon <- (naip_multispectral_mon[[4]] - naip_multispectral_mon[[1]]) / (naip_multispectral_mon[[4]] + naip_multispectral_mon[[1]])

# plot the data
plot(naip_ndvi_mon,
     main = "NDVI of Monrovia, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mon,
  main = "NDVI: Distribution of pixels\n NAIP Monrovia, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mop <- stack("~/GreenSpace_Thesis/Google Earth Images/Monterey Park, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mop <- brick(naip_multispectral_mop)

# calculate ndvi with naip
naip_multispectral_mop[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mop <- (naip_multispectral_mop[[4]] - naip_multispectral_mop[[1]]) / (naip_multispectral_mop[[4]] + naip_multispectral_mop[[1]])

# plot the data
plot(naip_ndvi_mop,
     main = "NDVI of Monterey Park, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mop,
  main = "NDVI: Distribution of pixels\n NAIP Monterey Park, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mont <- stack("~/GreenSpace_Thesis/Google Earth Images/Monterey, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mont <- brick(naip_multispectral_mont)

# calculate ndvi with naip
naip_multispectral_mont[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mont <- (naip_multispectral_mont[[4]] - naip_multispectral_mont[[1]]) / (naip_multispectral_mont[[4]] + naip_multispectral_mont[[1]])

# plot the data
plot(naip_ndvi_mont,
     main = "NDVI of Monterey, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mont,
  main = "NDVI: Distribution of pixels\n NAIP Monterey, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_moo <- stack("~/GreenSpace_Thesis/Google Earth Images/Moorpark, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_moo <- brick(naip_multispectral_moo)

# calculate ndvi with naip
naip_multispectral_moo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_moo <- (naip_multispectral_moo[[4]] - naip_multispectral_moo[[1]]) / (naip_multispectral_moo[[4]] + naip_multispectral_moo[[1]])

# plot the data
plot(naip_ndvi_moo,
     main = "NDVI of Moorpark, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_moo,
  main = "NDVI: Distribution of pixels\n NAIP Moorpark, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mor <- stack("~/GreenSpace_Thesis/Google Earth Images/Morgan Hill, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mor <- brick(naip_multispectral_mor)

# calculate ndvi with naip
naip_multispectral_mor[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mor <- (naip_multispectral_mor[[4]] - naip_multispectral_mor[[1]]) / (naip_multispectral_mor[[4]] + naip_multispectral_mor[[1]])

# plot the data
plot(naip_ndvi_mor,
     main = "NDVI of Morgan Hill, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mor,
  main = "NDVI: Distribution of pixels\n NAIP Morgan Hill, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mori <- stack("~/GreenSpace_Thesis/Google Earth Images/Morioka, Japan.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mori <- brick(naip_multispectral_mori)

# calculate ndvi with naip
naip_multispectral_mori[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mori <- (naip_multispectral_mori[[4]] - naip_multispectral_mori[[1]]) / (naip_multispectral_mori[[4]] + naip_multispectral_mori[[1]])

# plot the data
plot(naip_ndvi_mori,
     main = "NDVI of Morioka, Japan",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mori,
  main = "NDVI: Distribution of pixels\n NAIP Morioka, Japan",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mrd <- stack("~/GreenSpace_Thesis/Google Earth Images/Mountain Rd, Newbury NH.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mrd <- brick(naip_multispectral_mrd)

# calculate ndvi with naip
naip_multispectral_mrd[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mrd <- (naip_multispectral_mrd[[4]] - naip_multispectral_mrd[[1]]) / (naip_multispectral_mrd[[4]] + naip_multispectral_mrd[[1]])

# plot the data
plot(naip_ndvi_mrd,
     main = "NDVI of Mountain Rd, Newbury NH",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mrd,
  main = "NDVI: Distribution of pixels\n NAIP Mountain Rd, Newbury NH",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mv <- stack("~/GreenSpace_Thesis/Google Earth Images/Mountain View, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mv <- brick(naip_multispectral_mv)

# calculate ndvi with naip
naip_multispectral_mv[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mv <- (naip_multispectral_mv[[4]] - naip_multispectral_mv[[1]]) / (naip_multispectral_mv[[4]] + naip_multispectral_mv[[1]])

# plot the data
plot(naip_ndvi_mv,
     main = "NDVI of Mountain View, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mv,
  main = "NDVI: Distribution of pixels\n NAIP Mountain View, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_muk <- stack("~/GreenSpace_Thesis/Google Earth Images/Mukilteo, WA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_muk <- brick(naip_multispectral_muk)

# calculate ndvi with naip
naip_multispectral_muk[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_muk <- (naip_multispectral_muk[[4]] - naip_multispectral_muk[[1]]) / (naip_multispectral_muk[[4]] + naip_multispectral_muk[[1]])

# plot the data
plot(naip_ndvi_muk,
     main = "NDVI of Mukilteo, WA ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_muk,
  main = "NDVI: Distribution of pixels\n NAIP Mukilteo, WA ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mum <- stack("~/GreenSpace_Thesis/Google Earth Images/Mumbai, India.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mum <- brick(naip_multispectral_mum)

# calculate ndvi with naip
naip_multispectral_mum[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mum <- (naip_multispectral_mum[[4]] - naip_multispectral_mum[[1]]) / (naip_multispectral_mum[[4]] + naip_multispectral_mum[[1]])

# plot the data
plot(naip_ndvi_mum,
     main = "NDVI of Mumbai, India",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mum,
  main = "NDVI: Distribution of pixels\n NAIP Mumbai, India",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_mur <- stack("~/GreenSpace_Thesis/Google Earth Images/Murrieta, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_mur <- brick(naip_multispectral_mur)

# calculate ndvi with naip
naip_multispectral_mur[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_mur <- (naip_multispectral_mur[[4]] - naip_multispectral_mur[[1]]) / (naip_multispectral_mur[[4]] + naip_multispectral_mur[[1]])

# plot the data
plot(naip_ndvi_mur,
     main = "NDVI of Murrieta, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_mur,
  main = "NDVI: Distribution of pixels\n NAIP Murrieta, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_nam <- stack("~/GreenSpace_Thesis/Google Earth Images/Namyangju-si, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nam <- brick(naip_multispectral_nam)

# calculate ndvi with naip
naip_multispectral_nam[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nam <- (naip_multispectral_nam[[4]] - naip_multispectral_nam[[1]]) / (naip_multispectral_nam[[4]] + naip_multispectral_nam[[1]])

# plot the data
plot(naip_ndvi_nam,
     main = "NDVI of Namyangju-si, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nam,
  main = "NDVI: Distribution of pixels\n NAIP Namyangju-si, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_nan <- stack("~/GreenSpace_Thesis/Google Earth Images/Nancheng, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nan <- brick(naip_multispectral_nan)

# calculate ndvi with naip
naip_multispectral_nan[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nan <- (naip_multispectral_nan[[4]] - naip_multispectral_nan[[1]]) / (naip_multispectral_nan[[4]] + naip_multispectral_nan[[1]])

# plot the data
plot(naip_ndvi_nan,
     main = "NDVI of Nancheng, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nan,
  main = "NDVI: Distribution of pixels\n NAIP Nancheng, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_nanj <- stack("~/GreenSpace_Thesis/Google Earth Images/Nanjing, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nanj <- brick(naip_multispectral_nanj)

# calculate ndvi with naip
naip_multispectral_nanj[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nanj <- (naip_multispectral_nanj[[4]] - naip_multispectral_nanj[[1]]) / (naip_multispectral_nanj[[4]] + naip_multispectral_nanj[[1]])

# plot the data
plot(naip_ndvi_nanj,
     main = "NDVI of Nanjing, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nanj,
  main = "NDVI: Distribution of pixels\n NAIP Nanjing, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_nap <- stack("~/GreenSpace_Thesis/Google Earth Images/Napa, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nap <- brick(naip_multispectral_nap)

# calculate ndvi with naip
naip_multispectral_nap[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nap <- (naip_multispectral_nap[[4]] - naip_multispectral_nap[[1]]) / (naip_multispectral_nap[[4]] + naip_multispectral_nap[[1]])

# plot the data
plot(naip_ndvi_nap,
     main = "NDVI of Napa, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nap,
  main = "NDVI: Distribution of pixels\n NAIP Napa, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_napr <- stack("~/GreenSpace_Thesis/Google Earth Images/Naperville, IL.png")
# convert data into rasterbrick for faster processing

naip_multispectral_napr <- brick(naip_multispectral_napr)

# calculate ndvi with naip
naip_multispectral_napr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_napr <- (naip_multispectral_napr[[4]] - naip_multispectral_napr[[1]]) / (naip_multispectral_napr[[4]] + naip_multispectral_napr[[1]])

# plot the data
plot(naip_ndvi_napr,
     main = "NDVI of Naperville, IL",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_napr,
  main = "NDVI: Distribution of pixels\n NAIP Naperville, IL",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_new <- stack("~/GreenSpace_Thesis/Google Earth Images/New Delhi, Delhi, India.png")
# convert data into rasterbrick for faster processing

naip_multispectral_new <- brick(naip_multispectral_new)

# calculate ndvi with naip
naip_multispectral_new[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_new <- (naip_multispectral_new[[4]] - naip_multispectral_new[[1]]) / (naip_multispectral_new[[4]] + naip_multispectral_new[[1]])

# plot the data
plot(naip_ndvi_new,
     main = "NDVI of New Delhi, Delhi, India",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_new,
  main = "NDVI: Distribution of pixels\n NAIP New Delhi, Delhi, India",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_newr <- stack("~/GreenSpace_Thesis/Google Earth Images/New Port Richey, FL.png")
# convert data into rasterbrick for faster processing

naip_multispectral_newr <- brick(naip_multispectral_newr)

# calculate ndvi with naip
naip_multispectral_newr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_newr <- (naip_multispectral_newr[[4]] - naip_multispectral_newr[[1]]) / (naip_multispectral_newr[[4]] + naip_multispectral_newr[[1]])

# plot the data
plot(naip_ndvi_newr,
     main = "NDVI of New Port Richey, FL",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_newr,
  main = "NDVI: Distribution of pixels\n NAIP New Port Richey, FL",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_newp <- stack("~/GreenSpace_Thesis/Google Earth Images/Newport Beach, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_newp <- brick(naip_multispectral_newp)

# calculate ndvi with naip
naip_multispectral_newp[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_newp <- (naip_multispectral_newp[[4]] - naip_multispectral_newp[[1]]) / (naip_multispectral_newp[[4]] + naip_multispectral_newp[[1]])

# plot the data
plot(naip_ndvi_newp,
     main = "NDVI of Newport Beach, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_newp,
  main = "NDVI: Distribution of pixels\n NAIP Newport Beach, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_nor <- stack("~/GreenSpace_Thesis/Google Earth Images/North Hollywood, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nor <- brick(naip_multispectral_nor)

# calculate ndvi with naip
naip_multispectral_nor[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nor <- (naip_multispectral_nor[[4]] - naip_multispectral_nor[[1]]) / (naip_multispectral_nor[[4]] + naip_multispectral_nor[[1]])

# plot the data
plot(naip_ndvi_nor,
     main = "NDVI of North Hollywood, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nor,
  main = "NDVI: Distribution of pixels\n NAIP North Hollywood, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_nort <- stack("~/GreenSpace_Thesis/Google Earth Images/Norton, MA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nort <- brick(naip_multispectral_nort)

# calculate ndvi with naip
naip_multispectral_nort[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nort <- (naip_multispectral_nort[[4]] - naip_multispectral_nort[[1]]) / (naip_multispectral_nort[[4]] + naip_multispectral_nort[[1]])

# plot the data
plot(naip_ndvi_nort,
     main = "NDVI of Norton,MA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nort,
  main = "NDVI: Distribution of pixels\n NAIP Norton, MA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_nov <- stack("~/GreenSpace_Thesis/Google Earth Images/Novato, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_nov <- brick(naip_multispectral_nov)

# calculate ndvi with naip
naip_multispectral_nov[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_nov <- (naip_multispectral_nov[[4]] - naip_multispectral_nov[[1]]) / (naip_multispectral_nov[[4]] + naip_multispectral_nov[[1]])

# plot the data
plot(naip_ndvi_nov,
     main = "NDVI of Novato, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_nov,
  main = "NDVI: Distribution of pixels\n NAIP Novato, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_op <- stack("~/GreenSpace_Thesis/Google Earth Images/Oak Park, CA .png")
# convert data into rasterbrick for faster processing

naip_multispectral_op <- brick(naip_multispectral_op)

# calculate ndvi with naip
naip_multispectral_op[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_op <- (naip_multispectral_op[[4]] - naip_multispectral_op[[1]]) / (naip_multispectral_op[[4]] + naip_multispectral_op[[1]])

# plot the data
plot(naip_ndvi_op,
     main = "NDVI of Oak Park, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_op,
  main = "NDVI: Distribution of pixels\n NAIP Oak Park, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_oa <- stack("~/GreenSpace_Thesis/Google Earth Images/Oakland, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_oa <- brick(naip_multispectral_oa)

# calculate ndvi with naip
naip_multispectral_oa[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_oa <- (naip_multispectral_oa[[4]] - naip_multispectral_oa[[1]]) / (naip_multispectral_oa[[4]] + naip_multispectral_oa[[1]])

# plot the data
plot(naip_ndvi_oa,
     main = "NDVI of Oakland, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_oa,
  main = "NDVI: Distribution of pixels\n NAIP Oakland, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_oak <- stack("~/GreenSpace_Thesis/Google Earth Images/Oakley, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_oak <- brick(naip_multispectral_oak)

# calculate ndvi with naip
naip_multispectral_oak[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_oak <- (naip_multispectral_oak[[4]] - naip_multispectral_oak[[1]]) / (naip_multispectral_oak[[4]] + naip_multispectral_oak[[1]])

# plot the data
plot(naip_ndvi_oak,
     main = "NDVI of Oakley, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_oak,
  main = "NDVI: Distribution of pixels\n NAIP Oakley, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_oj <- stack("~/GreenSpace_Thesis/Google Earth Images/Ojai, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_oj <- brick(naip_multispectral_oj)

# calculate ndvi with naip
naip_multispectral_oj[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_oj <- (naip_multispectral_oj[[4]] - naip_multispectral_oj[[1]]) / (naip_multispectral_oj[[4]] + naip_multispectral_oj[[1]])

# plot the data
plot(naip_ndvi_oj,
     main = "NDVI of Ojai, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_oj,
  main = "NDVI: Distribution of pixels\n NAIP Ojai, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ok <- stack("~/GreenSpace_Thesis/Google Earth Images/Oksu-dong, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ok <- brick(naip_multispectral_ok)

# calculate ndvi with naip
naip_multispectral_ok[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ok <- (naip_multispectral_ok[[4]] - naip_multispectral_ok[[1]]) / (naip_multispectral_ok[[4]] + naip_multispectral_ok[[1]])

# plot the data
plot(naip_ndvi_ok,
     main = "NDVI of Oksu-dong, SK",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ok,
  main = "NDVI: Distribution of pixels\n NAIP Oksu-dong, SK",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ol <- stack("~/GreenSpace_Thesis/Google Earth Images/Olympia, WA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ol <- brick(naip_multispectral_ol)

# calculate ndvi with naip
naip_multispectral_ol[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ol <- (naip_multispectral_ol[[4]] - naip_multispectral_ol[[1]]) / (naip_multispectral_ol[[4]] + naip_multispectral_ol[[1]])

# plot the data
plot(naip_ndvi_ol,
     main = "NDVI of Olympia, WA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ol,
  main = "NDVI: Distribution of pixels\n NAIP Olympia, WA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_or <- stack("~/GreenSpace_Thesis/Google Earth Images/Orange, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_or <- brick(naip_multispectral_or)

# calculate ndvi with naip
naip_multispectral_or[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_or <- (naip_multispectral_or[[4]] - naip_multispectral_or[[1]]) / (naip_multispectral_or[[4]] + naip_multispectral_or[[1]])

# plot the data
plot(naip_ndvi_or,
     main = "NDVI of Orange, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_or,
  main = "NDVI: Distribution of pixels\n NAIP Orange, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_orl <- stack("~/GreenSpace_Thesis/Google Earth Images/Orleans, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_orl <- brick(naip_multispectral_orl)

# calculate ndvi with naip
naip_multispectral_orl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_orl <- (naip_multispectral_orl[[4]] - naip_multispectral_orl[[1]]) / (naip_multispectral_orl[[4]] + naip_multispectral_orl[[1]])

# plot the data
plot(naip_ndvi_orl,
     main = "NDVI of Orleans, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_orl,
  main = "NDVI: Distribution of pixels\n NAIP Orleans, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ory <- stack("~/GreenSpace_Thesis/Google Earth Images/Oryun-dong, SK.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ory <- brick(naip_multispectral_ory)

# calculate ndvi with naip
naip_multispectral_ory[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ory <- (naip_multispectral_ory[[4]] - naip_multispectral_ory[[1]]) / (naip_multispectral_ory[[4]] + naip_multispectral_ory[[1]])

# plot the data
plot(naip_ndvi_ory,
     main = "NDVI of Oryun-dong, South Korea",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ory,
  main = "NDVI: Distribution of pixels\n NAIP Oryun-dong, South Korea",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ov <- stack("~/GreenSpace_Thesis/Google Earth Images/Overland Park, KS.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ov <- brick(naip_multispectral_ov)

# calculate ndvi with naip
naip_multispectral_ov[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ov <- (naip_multispectral_ov[[4]] - naip_multispectral_ov[[1]]) / (naip_multispectral_ov[[4]] + naip_multispectral_ov[[1]])

# plot the data
plot(naip_ndvi_ov,
     main = "NDVI of Overland Park, KS",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ov,
  main = "NDVI: Distribution of pixels\n NAIP Overland Park, KS",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ox <- stack("~/GreenSpace_Thesis/Google Earth Images/Oxnard, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ox <- brick(naip_multispectral_ox)

# calculate ndvi with naip
naip_multispectral_ox[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ox <- (naip_multispectral_ox[[4]] - naip_multispectral_ox[[1]]) / (naip_multispectral_ox[[4]] + naip_multispectral_ox[[1]])

# plot the data
plot(naip_ndvi_ox,
     main = "NDVI of Oxnard, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ox,
  main = "NDVI: Distribution of pixels\n NAIP Oxnard, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
```

```{r}
# import the naip pre-fire data
naip_multispectral_pc <- stack("~/GreenSpace_Thesis/Google Earth Images/Pacific Palisades, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pc <- brick(naip_multispectral_pc)

# calculate ndvi with naip
naip_multispectral_pc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pc <- (naip_multispectral_pc[[4]] - naip_multispectral_pc[[1]]) / (naip_multispectral_pc[[4]] + naip_multispectral_pc[[1]])

# plot the data
plot(naip_ndvi_pc,
     main = "NDVI of Pacific Palisades, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pc,
  main = "NDVI: Distribution of pixels\n NAIP Pacific Palisades, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_pa <- stack("~/GreenSpace_Thesis/Google Earth Images/Palo Alto, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pa <- brick(naip_multispectral_pa)

# calculate ndvi with naip
naip_multispectral_pa[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pa <- (naip_multispectral_pa[[4]] - naip_multispectral_pa[[1]]) / (naip_multispectral_pa[[4]] + naip_multispectral_pa[[1]])

# plot the data
plot(naip_ndvi_pa,
     main = "NDVI of Palo Alto, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pa,
  main = "NDVI: Distribution of pixels\n NAIP Palo Alto, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pave <- stack("~/GreenSpace_Thesis/Google Earth Images/Palos Verdes Estates, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pave <- brick(naip_multispectral_pave)

# calculate ndvi with naip
naip_multispectral_pa[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pave <- (naip_multispectral_pave[[4]] - naip_multispectral_pave[[1]]) / (naip_multispectral_pave[[4]] + naip_multispectral_pave[[1]])

# plot the data
plot(naip_ndvi_pave,
     main = "NDVI of Palos Verdes Estates, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pave,
  main = "NDVI: Distribution of pixels\n NAIP Palos Verdes Estates, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pv <- stack("~/GreenSpace_Thesis/Google Earth Images/Palos Verdes, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pv <- brick(naip_multispectral_pv)

# calculate ndvi with naip
naip_multispectral_pv[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pv <- (naip_multispectral_pv[[4]] - naip_multispectral_pv[[1]]) / (naip_multispectral_pv[[4]] + naip_multispectral_pv[[1]])

# plot the data
plot(naip_ndvi_pv,
     main = "NDVI of Palos Verdes, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pv,
  main = "NDVI: Distribution of pixels\n NAIP Palos Verdes, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_pap <- stack("~/GreenSpace_Thesis/Google Earth Images/Parsippany, NJ.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pap <- brick(naip_multispectral_pap)

# calculate ndvi with naip
naip_multispectral_pap[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pap <- (naip_multispectral_pap[[4]] - naip_multispectral_pap[[1]]) / (naip_multispectral_pap[[4]] + naip_multispectral_pap[[1]])

# plot the data
plot(naip_ndvi_pap,
     main = "NDVI of Parsippany, NJ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pap,
  main = "NDVI: Distribution of pixels\n NAIP Parsippany, NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pas <- stack("~/GreenSpace_Thesis/Google Earth Images/Pasadena, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pas <- brick(naip_multispectral_pas)

# calculate ndvi with naip
naip_multispectral_pas[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pas <- (naip_multispectral_pas[[4]] - naip_multispectral_pas[[1]]) / (naip_multispectral_pas[[4]] + naip_multispectral_pas[[1]])

# plot the data
plot(naip_ndvi_pas,
     main = "NDVI of Pasadena, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pas,
  main = "NDVI: Distribution of pixels\n NAIP Pasadena, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pe <- stack("~/GreenSpace_Thesis/Google Earth Images/Penang, Malaysia.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pe <- brick(naip_multispectral_pe)

# calculate ndvi with naip
naip_multispectral_pe[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pe <- (naip_multispectral_pe[[4]] - naip_multispectral_pe[[1]]) / (naip_multispectral_pe[[4]] + naip_multispectral_pe[[1]])

# plot the data
plot(naip_ndvi_pe,
     main = "NDVI of Penang, Malaysia",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pe,
  main = "NDVI: Distribution of pixels\n NAIP Pennang, Malaysia",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pet <- stack("~/GreenSpace_Thesis/Google Earth Images/Petaluma, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pet <- brick(naip_multispectral_pet)

# calculate ndvi with naip
naip_multispectral_pet[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pet <- (naip_multispectral_pet[[4]] - naip_multispectral_pet[[1]]) / (naip_multispectral_pet[[4]] + naip_multispectral_pet[[1]])

# plot the data
plot(naip_ndvi_pet,
     main = "NDVI of Petaluma, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pet,
  main = "NDVI: Distribution of pixels\n NAIP Petaluma, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ph <- stack("~/GreenSpace_Thesis/Google Earth Images/Phoenix, AX.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ph <- brick(naip_multispectral_ph)

# calculate ndvi with naip
naip_multispectral_ph[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ph <- (naip_multispectral_ph[[4]] - naip_multispectral_ph[[1]]) / (naip_multispectral_ph[[4]] + naip_multispectral_ph[[1]])

# plot the data
plot(naip_ndvi_ph,
     main = "NDVI of Phoenix, AZ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ph,
  main = "NDVI: Distribution of pixels\n NAIP Phoenix, AZ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pi <- stack("~/GreenSpace_Thesis/Google Earth Images/Pinole, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pi <- brick(naip_multispectral_pi)

# calculate ndvi with naip
naip_multispectral_pi[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pi <- (naip_multispectral_pi[[4]] - naip_multispectral_pi[[1]]) / (naip_multispectral_pi[[4]] + naip_multispectral_pi[[1]])

# plot the data
plot(naip_ndvi_pi,
     main = "NDVI of Pinole, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pi,
  main = "NDVI: Distribution of pixels\n NAIP Pinole, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pl <- stack("~/GreenSpace_Thesis/Google Earth Images/Placerville, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pl <- brick(naip_multispectral_pl)

# calculate ndvi with naip
naip_multispectral_pl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pl <- (naip_multispectral_pl[[4]] - naip_multispectral_pl[[1]]) / (naip_multispectral_pl[[4]] + naip_multispectral_pl[[1]])

# plot the data
plot(naip_ndvi_pl,
     main = "NDVI of Placerville, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pl,
  main = "NDVI: Distribution of pixels\n NAIP Placerville, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_ple <- stack("~/GreenSpace_Thesis/Google Earth Images/Pleasanton, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ple <- brick(naip_multispectral_ple)

# calculate ndvi with naip
naip_multispectral_ple[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ple <- (naip_multispectral_ple[[4]] - naip_multispectral_ple[[1]]) / (naip_multispectral_ple[[4]] + naip_multispectral_ple[[1]])

# plot the data
plot(naip_ndvi_ple,
     main = "NDVI of Pleasanton, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ple,
  main = "NDVI: Distribution of pixels\n NAIP Pleasanton, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pp <- stack("~/GreenSpace_Thesis/Google Earth Images/Point Pleasant, NJ.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pp <- brick(naip_multispectral_pp)

# calculate ndvi with naip
naip_multispectral_pp[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pp <- (naip_multispectral_pp[[4]] - naip_multispectral_pp[[1]]) / (naip_multispectral_pp[[4]] + naip_multispectral_pp[[1]])

# plot the data
plot(naip_ndvi_pp,
     main = "NDVI of Point Pleasant, NJ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pp,
  main = "NDVI: Distribution of pixels\n NAIP Point Pleasant, NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_po <- stack("~/GreenSpace_Thesis/Google Earth Images/Pompano Beach, FL.png")
# convert data into rasterbrick for faster processing

naip_multispectral_po <- brick(naip_multispectral_po)

# calculate ndvi with naip
naip_multispectral_po[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_po <- (naip_multispectral_po[[4]] - naip_multispectral_po[[1]]) / (naip_multispectral_po[[4]] + naip_multispectral_po[[1]])

# plot the data
plot(naip_ndvi_po,
     main = "NDVI of Pompano Beach, FL",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_po,
  main = "NDVI: Distribution of pixels\n NAIP Pompano Beahc, FL",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pm <- stack("~/GreenSpace_Thesis/Google Earth Images/Port Moody, Canada.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pm <- brick(naip_multispectral_pm)

# calculate ndvi with naip
naip_multispectral_pm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pm <- (naip_multispectral_pm[[4]] - naip_multispectral_pm[[1]]) / (naip_multispectral_pm[[4]] + naip_multispectral_pm[[1]])

# plot the data
plot(naip_ndvi_pm,
     main = "NDVI of Port Moody, Canada",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pm,
  main = "NDVI: Distribution of pixels\n NAIP Port Moody, Canada",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_por <- stack("~/GreenSpace_Thesis/Google Earth Images/Portland, OR.png")
# convert data into rasterbrick for faster processing

naip_multispectral_por <- brick(naip_multispectral_por)

# calculate ndvi with naip
naip_multispectral_por[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_por <- (naip_multispectral_por[[4]] - naip_multispectral_por[[1]]) / (naip_multispectral_por[[4]] + naip_multispectral_por[[1]])

# plot the data
plot(naip_ndvi_por,
     main = "NDVI of Portland, OR",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_por,
  main = "NDVI: Distribution of pixels\n NAIP Portland, OR",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_pr <- stack("~/GreenSpace_Thesis/Google Earth Images/Pound Ridge, NY.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pr <- brick(naip_multispectral_pr)

# calculate ndvi with naip
naip_multispectral_pr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pr <- (naip_multispectral_pr[[4]] - naip_multispectral_pr[[1]]) / (naip_multispectral_pr[[4]] + naip_multispectral_pr[[1]])

# plot the data
plot(naip_ndvi_pr,
     main = "NDVI of Pound Ridge, NY",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pr,
  main = "NDVI: Distribution of pixels\n NAIP Pound Ridge, NY",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pri <- stack("~/GreenSpace_Thesis/Google Earth Images/Princeton, NJ.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pri <- brick(naip_multispectral_pri)

# calculate ndvi with naip
naip_multispectral_pri[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pri <- (naip_multispectral_pri[[4]] - naip_multispectral_pri[[1]]) / (naip_multispectral_pri[[4]] + naip_multispectral_pri[[1]])

# plot the data
plot(naip_ndvi_pri,
     main = "NDVI of Princeton, NJ",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pri,
  main = "NDVI: Distribution of pixels\n NAIP Princeton, NJ",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pu <- stack("~/GreenSpace_Thesis/Google Earth Images/Pune, India.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pu <- brick(naip_multispectral_pu)

# calculate ndvi with naip
naip_multispectral_pu[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pu <- (naip_multispectral_pu[[4]] - naip_multispectral_pu[[1]]) / (naip_multispectral_pu[[4]] + naip_multispectral_pu[[1]])

# plot the data
plot(naip_ndvi_pu,
     main = "NDVI of Pune, INdia",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pu,
  main = "NDVI: Distribution of pixels\n NAIP Pune, India",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_pb <- stack("~/GreenSpace_Thesis/Google Earth Images/Punjabi Bagh.png")
# convert data into rasterbrick for faster processing

naip_multispectral_pb <- brick(naip_multispectral_pb)

# calculate ndvi with naip
naip_multispectral_pb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_pb <- (naip_multispectral_pb[[4]] - naip_multispectral_pb[[1]]) / (naip_multispectral_pb[[4]] + naip_multispectral_pb[[1]])

# plot the data
plot(naip_ndvi_pb,
     main = "NDVI of Punjabi Bagh",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_pb,
  main = "NDVI: Distribution of pixels\n NAIP Punjabi Bagh",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_q <- stack("~/GreenSpace_Thesis/Google Earth Images/Qingdao, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_q <- brick(naip_multispectral_q)

# calculate ndvi with naip
naip_multispectral_q[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_q <- (naip_multispectral_q[[4]] - naip_multispectral_q[[1]]) / (naip_multispectral_q[[4]] + naip_multispectral_q[[1]])

# plot the data
plot(naip_ndvi_q,
     main = "NDVI of Qingdao, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_q,
  main = "NDVI: Distribution of pixels\n NAIP Qingdao, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_rc <- stack("~/GreenSpace_Thesis/Google Earth Images/Rancho Cordova, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_rc <- brick(naip_multispectral_rc)

# calculate ndvi with naip
naip_multispectral_rc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_rc <- (naip_multispectral_rc[[4]] - naip_multispectral_rc[[1]]) / (naip_multispectral_rc[[4]] + naip_multispectral_rc[[1]])

# plot the data
plot(naip_ndvi_rc,
     main = "NDVI of Rancho Cordova, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_rc,
  main = "NDVI: Distribution of pixels\n NAIP Rancho Cordova, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_rcu <- stack("~/GreenSpace_Thesis/Google Earth Images/Rancho Cucamonga, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_rcu <- brick(naip_multispectral_rcu)

# calculate ndvi with naip
naip_multispectral_rcu[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_rcu <- (naip_multispectral_rcu[[4]] - naip_multispectral_rcu[[1]]) / (naip_multispectral_rcu[[4]] + naip_multispectral_rcu[[1]])

# plot the data
plot(naip_ndvi_rcu,
     main = "NDVI of Rancho Cucamonga, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_rcu,
  main = "NDVI: Distribution of pixels\n NAIP Rancho Cucamonga, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_re <- stack("~/GreenSpace_Thesis/Google Earth Images/Redlands, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_re <- brick(naip_multispectral_re)

# calculate ndvi with naip
naip_multispectral_re[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_re <- (naip_multispectral_re[[4]] - naip_multispectral_re[[1]]) / (naip_multispectral_re[[4]] + naip_multispectral_re[[1]])

# plot the data
plot(naip_ndvi_re,
     main = "NDVI of Redlands, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_re,
  main = "NDVI: Distribution of pixels\n NAIP Redlands, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_rw <- stack("~/GreenSpace_Thesis/Google Earth Images/Redwood City, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_rw <- brick(naip_multispectral_rw)

# calculate ndvi with naip
naip_multispectral_rw[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_rw <- (naip_multispectral_rw[[4]] - naip_multispectral_rw[[1]]) / (naip_multispectral_rw[[4]] + naip_multispectral_rw[[1]])

# plot the data
plot(naip_ndvi_rw,
     main = "NDVI of Redwood City, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_rw,
  main = "NDVI: Distribution of pixels\n NAIP Redwood City, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_ri <- stack("~/GreenSpace_Thesis/Google Earth Images/Riverside, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_ri <- brick(naip_multispectral_ri)

# calculate ndvi with naip
naip_multispectral_ri[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_ri <- (naip_multispectral_ri[[4]] - naip_multispectral_ri[[1]]) / (naip_multispectral_ri[[4]] + naip_multispectral_ri[[1]])

# plot the data
plot(naip_ndvi_ri,
     main = "NDVI of Riverside, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_ri,
  main = "NDVI: Distribution of pixels\n NAIP Riverside, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_rob <- stack("~/GreenSpace_Thesis/Google Earth Images/Robbinsdale, MN.png")
# convert data into rasterbrick for faster processing

naip_multispectral_rob <- brick(naip_multispectral_rob)

# calculate ndvi with naip
naip_multispectral_rob[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_rob <- (naip_multispectral_rob[[4]] - naip_multispectral_rob[[1]]) / (naip_multispectral_rob[[4]] + naip_multispectral_rob[[1]])

# plot the data
plot(naip_ndvi_rob,
     main = "NDVI of Robbinsdale, MN",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_rob,
  main = "NDVI: Distribution of pixels\n NAIP Robbinsdale, MN",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_roc <- stack("~/GreenSpace_Thesis/Google Earth Images/Rocklin, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_roc <- brick(naip_multispectral_roc)

# calculate ndvi with naip
naip_multispectral_roc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_roc <- (naip_multispectral_roc[[4]] - naip_multispectral_roc[[1]]) / (naip_multispectral_roc[[4]] + naip_multispectral_roc[[1]])

# plot the data
plot(naip_ndvi_roc,
     main = "NDVI of Rocklin, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_roc,
  main = "NDVI: Distribution of pixels\n NAIP Rocklin, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_rod <- stack("~/GreenSpace_Thesis/Google Earth Images/Rodeo, CA .png")
# convert data into rasterbrick for faster processing

naip_multispectral_rod <- brick(naip_multispectral_rod)

# calculate ndvi with naip
naip_multispectral_rod[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_rod <- (naip_multispectral_rod[[4]] - naip_multispectral_rod[[1]]) / (naip_multispectral_rod[[4]] + naip_multispectral_rod[[1]])

# plot the data
plot(naip_ndvi_rod,
     main = "NDVI of Rodeo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_rod,
  main = "NDVI: Distribution of pixels\n NAIP Rocdeo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sac <- stack("~/GreenSpace_Thesis/Google Earth Images/Sacramento, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sac <- brick(naip_multispectral_sac)

# calculate ndvi with naip
naip_multispectral_sac[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sac <- (naip_multispectral_sac[[4]] - naip_multispectral_sac[[1]]) / (naip_multispectral_sac[[4]] + naip_multispectral_sac[[1]])

# plot the data
plot(naip_ndvi_sac,
     main = "NDVI of Sacramento, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sac,
  main = "NDVI: Distribution of pixels\n NAIP Sacramento, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sm <- stack("~/GreenSpace_Thesis/Google Earth Images/Salem, IL.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sm <- brick(naip_multispectral_sm)

# calculate ndvi with naip
naip_multispectral_sm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sm <- (naip_multispectral_sm[[4]] - naip_multispectral_sm[[1]]) / (naip_multispectral_sm[[4]] + naip_multispectral_sm[[1]])

# plot the data
plot(naip_ndvi_sm,
     main = "NDVI of Salem, IL",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sm,
  main = "NDVI: Distribution of pixels\n NAIP Salem, IL",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sld <- stack("~/GreenSpace_Thesis/Google Earth Images/Salida, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sld <- brick(naip_multispectral_sld)

# calculate ndvi with naip
naip_multispectral_sld[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sld <- (naip_multispectral_sld[[4]] - naip_multispectral_sld[[1]]) / (naip_multispectral_sld[[4]] + naip_multispectral_sld[[1]])

# plot the data
plot(naip_ndvi_sld,
     main = "NDVI of Salida, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sld,
  main = "NDVI: Distribution of pixels\n NAIP Salida, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sln <- stack("~/GreenSpace_Thesis/Google Earth Images/Salinas, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sln <- brick(naip_multispectral_sln)

# calculate ndvi with naip
naip_multispectral_sln[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sln <- (naip_multispectral_sln[[4]] - naip_multispectral_sln[[1]]) / (naip_multispectral_sln[[4]] + naip_multispectral_sln[[1]])

# plot the data
plot(naip_ndvi_sln,
     main = "NDVI of Salinas, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sln,
  main = "NDVI: Distribution of pixels\n NAIP Salinas, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_slc <- stack("~/GreenSpace_Thesis/Google Earth Images/Salt Lake City, UT.png")
# convert data into rasterbrick for faster processing

naip_multispectral_slc <- brick(naip_multispectral_slc)

# calculate ndvi with naip
naip_multispectral_slc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_slc <- (naip_multispectral_slc[[4]] - naip_multispectral_slc[[1]]) / (naip_multispectral_slc[[4]] + naip_multispectral_slc[[1]])

# plot the data
plot(naip_ndvi_slc,
     main = "NDVI of Salt Lake City, UT",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slc,
  main = "NDVI: Distribution of pixels\n NAIP Salt Lake City, UT",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sbr <- stack("~/GreenSpace_Thesis/Google Earth Images/San Berdardinao, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sbr <- brick(naip_multispectral_sbr)

# calculate ndvi with naip
naip_multispectral_sbr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sbr <- (naip_multispectral_sbr[[4]] - naip_multispectral_sbr[[1]]) / (naip_multispectral_sbr[[4]] + naip_multispectral_sbr[[1]])

# plot the data
plot(naip_ndvi_sbr,
     main = "NDVI of San Bernardino, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sbr,
  main = "NDVI: Distribution of pixels\n NAIP San Bernardino, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sc <- stack("~/GreenSpace_Thesis/Google Earth Images/San Carlos, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sc <- brick(naip_multispectral_sc)

# calculate ndvi with naip
naip_multispectral_sc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sc <- (naip_multispectral_sc[[4]] - naip_multispectral_sc[[1]]) / (naip_multispectral_sc[[4]] + naip_multispectral_sc[[1]])

# plot the data
plot(naip_ndvi_sc,
     main = "NDVI of San Carlos, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sc,
  main = "NDVI: Distribution of pixels\n NAIP San Carlos, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_scc <- stack("~/GreenSpace_Thesis/Google Earth Images/San Clemente, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_scc <- brick(naip_multispectral_scc)

# calculate ndvi with naip
naip_multispectral_scc[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_scc <- (naip_multispectral_scc[[4]] - naip_multispectral_scc[[1]]) / (naip_multispectral_scc[[4]] + naip_multispectral_scc[[1]])

# plot the data
plot(naip_ndvi_scc,
     main = "NDVI of San Clemente, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_scc,
  main = "NDVI: Distribution of pixels\n NAIP San Clemente, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sd <- stack("~/GreenSpace_Thesis/Google Earth Images/San Diego, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sd <- brick(naip_multispectral_sd)

# calculate ndvi with naip
naip_multispectral_sd[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sd <- (naip_multispectral_sd[[4]] - naip_multispectral_sd[[1]]) / (naip_multispectral_sd[[4]] + naip_multispectral_sd[[1]])

# plot the data
plot(naip_ndvi_sd,
     main = "NDVI of San Diego, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sd,
  main = "NDVI: Distribution of pixels\n NAIP San Diego, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sfr <- stack("~/GreenSpace_Thesis/Google Earth Images/San Fernando, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sfr <- brick(naip_multispectral_sfr)

# calculate ndvi with naip
naip_multispectral_sfr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sfr <- (naip_multispectral_sfr[[4]] - naip_multispectral_sfr[[1]]) / (naip_multispectral_sfr[[4]] + naip_multispectral_sfr[[1]])

# plot the data
plot(naip_ndvi_sfr,
     main = "NDVI of San Fernando, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sfr,
  main = "NDVI: Distribution of pixels\n NAIP San Fernando, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sf <- stack("~/GreenSpace_Thesis/Google Earth Images/San Francisco, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sf <- brick(naip_multispectral_sf)

# calculate ndvi with naip
naip_multispectral_sf[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sf <- (naip_multispectral_sf[[4]] - naip_multispectral_sf[[1]]) / (naip_multispectral_sf[[4]] + naip_multispectral_sf[[1]])

# plot the data
plot(naip_ndvi_sf,
     main = "NDVI of San Francisco, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sf,
  main = "NDVI: Distribution of pixels\n NAIP San Francisco, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sg <- stack("~/GreenSpace_Thesis/Google Earth Images/San Gabriel, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sg <- brick(naip_multispectral_sg)

# calculate ndvi with naip
naip_multispectral_sg[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sg <- (naip_multispectral_sg[[4]] - naip_multispectral_sg[[1]]) / (naip_multispectral_sg[[4]] + naip_multispectral_sg[[1]])

# plot the data
plot(naip_ndvi_sg,
     main = "NDVI of San Gabriel, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sg,
  main = "NDVI: Distribution of pixels\n NAIP San Gabriel, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sj <- stack("~/GreenSpace_Thesis/Google Earth Images/San Jose, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sj <- brick(naip_multispectral_sj)

# calculate ndvi with naip
naip_multispectral_sj[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sj <- (naip_multispectral_sj[[4]] - naip_multispectral_sj[[1]]) / (naip_multispectral_sj[[4]] + naip_multispectral_sj[[1]])

# plot the data
plot(naip_ndvi_sj,
     main = "NDVI of San Jose, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sj,
  main = "NDVI: Distribution of pixels\n NAIP San Jose, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sl <- stack("~/GreenSpace_Thesis/Google Earth Images/San Leandro, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sl <- brick(naip_multispectral_sl)

# calculate ndvi with naip
naip_multispectral_sl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sl <- (naip_multispectral_sl[[4]] - naip_multispectral_sl[[1]]) / (naip_multispectral_sl[[4]] + naip_multispectral_sl[[1]])

# plot the data
plot(naip_ndvi_sl,
     main = "NDVI of San Leandro, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sl,
  main = "NDVI: Distribution of pixels\n NAIP San Leandro, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_slor <- stack("~/GreenSpace_Thesis/Google Earth Images/San Lorenzo, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_slor <- brick(naip_multispectral_slor)

# calculate ndvi with naip
naip_multispectral_slor[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_slor <- (naip_multispectral_slor[[4]] - naip_multispectral_slor[[1]]) / (naip_multispectral_slor[[4]] + naip_multispectral_slor[[1]])

# plot the data
plot(naip_ndvi_slor,
     main = "NDVI of San Lorenzo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slor,
  main = "NDVI: Distribution of pixels\n NAIP San Lorenzo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_slb <- stack("~/GreenSpace_Thesis/Google Earth Images/San Luis Obispo, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_slb <- brick(naip_multispectral_slb)

# calculate ndvi with naip
naip_multispectral_slb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_slb <- (naip_multispectral_slb[[4]] - naip_multispectral_slb[[1]]) / (naip_multispectral_slb[[4]] + naip_multispectral_slb[[1]])

# plot the data
plot(naip_ndvi_slb,
     main = "NDVI of San Luis Obispo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_slb,
  main = "NDVI: Distribution of pixels\n NAIP San Luis Obispo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_smr <- stack("~/GreenSpace_Thesis/Google Earth Images/San Marcos, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_smr <- brick(naip_multispectral_smr)

# calculate ndvi with naip
naip_multispectral_smr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_smr <- (naip_multispectral_smr[[4]] - naip_multispectral_smr[[1]]) / (naip_multispectral_smr[[4]] + naip_multispectral_smr[[1]])

# plot the data
plot(naip_ndvi_smr,
     main = "NDVI of San Marcos, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_smr,
  main = "NDVI: Distribution of pixels\n NAIP San Marcos, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_smt <- stack("~/GreenSpace_Thesis/Google Earth Images/San Mateo, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_smt <- brick(naip_multispectral_smt)

# calculate ndvi with naip
naip_multispectral_smt[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_smt <- (naip_multispectral_smt[[4]] - naip_multispectral_smt[[1]]) / (naip_multispectral_smt[[4]] + naip_multispectral_smt[[1]])

# plot the data
plot(naip_ndvi_smt,
     main = "NDVI of San Mateo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_smt,
  main = "NDVI: Distribution of pixels\n NAIP San Mateo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sp <- stack("~/GreenSpace_Thesis/Google Earth Images/San Pablo, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sp <- brick(naip_multispectral_sp)

# calculate ndvi with naip
naip_multispectral_sp[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sp <- (naip_multispectral_sp[[4]] - naip_multispectral_sp[[1]]) / (naip_multispectral_sp[[4]] + naip_multispectral_sp[[1]])

# plot the data
plot(naip_ndvi_sp,
     main = "NDVI of San Pablo, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sp,
  main = "NDVI: Distribution of pixels\n NAIP San Pablo, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_spe <- stack("~/GreenSpace_Thesis/Google Earth Images/San Pedro, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_spe <- brick(naip_multispectral_spe)

# calculate ndvi with naip
naip_multispectral_spe[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_spe <- (naip_multispectral_spe[[4]] - naip_multispectral_spe[[1]]) / (naip_multispectral_spe[[4]] + naip_multispectral_spe[[1]])

# plot the data
plot(naip_ndvi_spe,
     main = "NDVI of San Pedro, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_spe,
  main = "NDVI: Distribution of pixels\n NAIP San Pedro, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sr <- stack("~/GreenSpace_Thesis/Google Earth Images/San Rafael, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sr <- brick(naip_multispectral_sr)

# calculate ndvi with naip
naip_multispectral_sr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sr <- (naip_multispectral_sr[[4]] - naip_multispectral_sr[[1]]) / (naip_multispectral_sr[[4]] + naip_multispectral_sr[[1]])

# plot the data
plot(naip_ndvi_sr,
     main = "NDVI of San Rafael, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sr,
  main = "NDVI: Distribution of pixels\n NAIP San Rafael, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_srm <- stack("~/GreenSpace_Thesis/Google Earth Images/San Ramon, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_srm <- brick(naip_multispectral_srm)

# calculate ndvi with naip
naip_multispectral_srm[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_srm <- (naip_multispectral_srm[[4]] - naip_multispectral_srm[[1]]) / (naip_multispectral_srm[[4]] + naip_multispectral_srm[[1]])

# plot the data
plot(naip_ndvi_srm,
     main = "NDVI of San Ramon, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_srm,
  main = "NDVI: Distribution of pixels\n NAIP San Ramon, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sa <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Ana, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sa <- brick(naip_multispectral_sa)

# calculate ndvi with naip
naip_multispectral_sa[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sa <- (naip_multispectral_sa[[4]] - naip_multispectral_sa[[1]]) / (naip_multispectral_sa[[4]] + naip_multispectral_sa[[1]])

# plot the data
plot(naip_ndvi_sa,
     main = "NDVI of Santa Ana, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sa,
  main = "NDVI: Distribution of pixels\n NAIP Santa Ana, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sb <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Barbara, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sb <- brick(naip_multispectral_sb)

# calculate ndvi with naip
naip_multispectral_sb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sb <- (naip_multispectral_sb[[4]] - naip_multispectral_sb[[1]]) / (naip_multispectral_sb[[4]] + naip_multispectral_sb[[1]])

# plot the data
plot(naip_ndvi_sb,
     main = "NDVI of Santa Barbara, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sb,
  main = "NDVI: Distribution of pixels\n NAIP Santa Barbara, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_scl <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Clarita, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_scl <- brick(naip_multispectral_scl)

# calculate ndvi with naip
naip_multispectral_scl[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_scl <- (naip_multispectral_scl[[4]] - naip_multispectral_scl[[1]]) / (naip_multispectral_scl[[4]] + naip_multispectral_scl[[1]])

# plot the data
plot(naip_ndvi_scl,
     main = "NDVI of Santa Clarita, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_scl,
  main = "NDVI: Distribution of pixels\n NAIP Santa Clarita, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_scr <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Cruz, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_scr <- brick(naip_multispectral_scr)

# calculate ndvi with naip
naip_multispectral_scr[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_scr <- (naip_multispectral_scr[[4]] - naip_multispectral_scr[[1]]) / (naip_multispectral_scr[[4]] + naip_multispectral_scr[[1]])

# plot the data
plot(naip_ndvi_scr,
     main = "NDVI of Santa Cruz, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_scr,
  main = "NDVI: Distribution of pixels\n NAIP Santa Cruz, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sma <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Maria, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sma <- brick(naip_multispectral_sma)

# calculate ndvi with naip
naip_multispectral_sma[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sma <- (naip_multispectral_sma[[4]] - naip_multispectral_sma[[1]]) / (naip_multispectral_sma[[4]] + naip_multispectral_sma[[1]])

# plot the data
plot(naip_ndvi_sma,
     main = "NDVI of Santa Maria, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sma,
  main = "NDVI: Distribution of pixels\n NAIP Santa Maria, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_smo <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Monica, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_smo <- brick(naip_multispectral_smo)

# calculate ndvi with naip
naip_multispectral_smo[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_smo <- (naip_multispectral_smo[[4]] - naip_multispectral_smo[[1]]) / (naip_multispectral_smo[[4]] + naip_multispectral_smo[[1]])

# plot the data
plot(naip_ndvi_smo,
     main = "NDVI of Santa Monica, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_smo,
  main = "NDVI: Distribution of pixels\n NAIP Santa Monica, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_sro <- stack("~/GreenSpace_Thesis/Google Earth Images/Santa Rosa, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sro <- brick(naip_multispectral_sro)

# calculate ndvi with naip
naip_multispectral_sro[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sro <- (naip_multispectral_sro[[4]] - naip_multispectral_sro[[1]]) / (naip_multispectral_sro[[4]] + naip_multispectral_sro[[1]])

# plot the data
plot(naip_ndvi_sro,
     main = "NDVI of Santa Rosa, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sro,
  main = "NDVI: Distribution of pixels\n NAIP Santa Rosa, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_san <- stack("~/GreenSpace_Thesis/Google Earth Images/Santee, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_san <- brick(naip_multispectral_san)

# calculate ndvi with naip
naip_multispectral_san[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_san <- (naip_multispectral_san[[4]] - naip_multispectral_san[[1]]) / (naip_multispectral_san[[4]] + naip_multispectral_san[[1]])

# plot the data
plot(naip_ndvi_san,
     main = "NDVI of Santee, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_san,
  main = "NDVI: Distribution of pixels\n NAIP Santee, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sant <- stack("~/GreenSpace_Thesis/Google Earth Images/Santpoort-Noord, Netherlands.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sant <- brick(naip_multispectral_sant)

# calculate ndvi with naip
naip_multispectral_sant[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sant <- (naip_multispectral_sant[[4]] - naip_multispectral_sant[[1]]) / (naip_multispectral_sant[[4]] + naip_multispectral_sant[[1]])

# plot the data
plot(naip_ndvi_sant,
     main = "NDVI of Santpoort-Noord, Netherlands",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sant,
  main = "NDVI: Distribution of pixels\n NAIP Santpoort-Noord, Netherlands",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_spb <- stack("~/GreenSpace_Thesis/Google Earth Images/Sao Paulo, Brazil .png")
# convert data into rasterbrick for faster processing

naip_multispectral_spb <- brick(naip_multispectral_spb)

# calculate ndvi with naip
naip_multispectral_spb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_spb <- (naip_multispectral_spb[[4]] - naip_multispectral_spb[[1]]) / (naip_multispectral_spb[[4]] + naip_multispectral_spb[[1]])

# plot the data
plot(naip_ndvi_spb,
     main = "NDVI of Sao Paulo, Brazil",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_spb,
  main = "NDVI: Distribution of pixels\n NAIP Sao Paulo, Brazil",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sar <- stack("~/GreenSpace_Thesis/Google Earth Images/Saratoga, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sar <- brick(naip_multispectral_sar)

# calculate ndvi with naip
naip_multispectral_sar[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sar <- (naip_multispectral_sar[[4]] - naip_multispectral_sar[[1]]) / (naip_multispectral_sar[[4]] + naip_multispectral_sar[[1]])

# plot the data
plot(naip_ndvi_sar,
     main = "NDVI of Saratoga, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sar,
  main = "NDVI: Distribution of pixels\n NAIP Saratoga, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 
```{r}
# import the naip pre-fire data
naip_multispectral_sau <- stack("~/GreenSpace_Thesis/Google Earth Images/Saugus, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sau <- brick(naip_multispectral_sau)

# calculate ndvi with naip
naip_multispectral_sau[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sau <- (naip_multispectral_sau[[4]] - naip_multispectral_sau[[1]]) / (naip_multispectral_sau[[4]] + naip_multispectral_sau[[1]])

# plot the data
plot(naip_ndvi_sau,
     main = "NDVI of Saugus, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sau,
  main = "NDVI: Distribution of pixels\n NAIP Saugus, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_seb <- stack("~/GreenSpace_Thesis/Google Earth Images/Sebastopol, CA.png")
# convert data into rasterbrick for faster processing

naip_multispectral_seb <- brick(naip_multispectral_seb)

# calculate ndvi with naip
naip_multispectral_seb[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_seb <- (naip_multispectral_seb[[4]] - naip_multispectral_seb[[1]]) / (naip_multispectral_seb[[4]] + naip_multispectral_seb[[1]])

# plot the data
plot(naip_ndvi_seb,
     main = "NDVI of Sebastopol, CA",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_seb,
  main = "NDVI: Distribution of pixels\n NAIP Sebastopol, CA",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_sha <- stack("~/GreenSpace_Thesis/Google Earth Images/Shanghai, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_sha <- brick(naip_multispectral_sha)

# calculate ndvi with naip
naip_multispectral_sha[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_sha <- (naip_multispectral_sha[[4]] - naip_multispectral_sha[[1]]) / (naip_multispectral_sha[[4]] + naip_multispectral_sha[[1]])

# plot the data
plot(naip_ndvi_sha,
     main = "NDVI of Shanghai, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_sha,
  main = "NDVI: Distribution of pixels\n NAIP Shanghai, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 

```{r}
# import the naip pre-fire data
naip_multispectral_shap <- stack("~/GreenSpace_Thesis/Google Earth Images/Shapingba, China.png")
# convert data into rasterbrick for faster processing

naip_multispectral_shap <- brick(naip_multispectral_shap)

# calculate ndvi with naip
naip_multispectral_shap[[4]]

# calculate NDVI using the red (band 1) and nir (band 4) bands
naip_ndvi_shap <- (naip_multispectral_shap[[4]] - naip_multispectral_shap[[1]]) / (naip_multispectral_shap[[4]] + naip_multispectral_shap[[1]])

# plot the data
plot(naip_ndvi_shap,
     main = "NDVI of Shapingba, China",
     axes = FALSE, box = FALSE)

# view distribution of NDVI values
hist(naip_ndvi_shap,
  main = "NDVI: Distribution of pixels\n NAIP Shapingba, China",
  col = "springgreen",
  xlab = "NDVI Index Value")
``` 










**CORRECTION NEEDS TO BE MADE/NOTED, The scale of REFERENCE is one mile from Google Earth, the radius of the image captured is NOT 1 mile (the radius is closer to 4 or 5 miles)**

# Location Code List 

br5 = Berkeley, CA 5 miles 
br1 = Berkeley, CA 1 mile (94720)
elc = El Cerrito, CA 1 mile 
slc = Shenyang, Liaoning, China 1 mile 
blm = Billingstad, Norway 1 mile 
hny = Harlem, New York 1 mile 
poca = Poway, CA (92064)
scca = San Clemente, CA 1 mile (92673)
un = Union City, CA 1 mile (94587)
ado = Adelento, CA 1 mile
adie = Adikeih, Eritrea 1 mile
ala = Alameda, CA 1 mile 
alamo = Alamo, CA 1 mile
alb = Albany, CA 1 mile 
alh = Alhambra, CA 1 mile 
alta = Altadena, CA 1 mile 
ana = Anaheim, CA 1 mile 
ap = Apple Valley, CA 1 mile 
temp = Temple City, CA 1 mile 
arc = Arcadia City, CA 1 mile 
aus = Austin, TX 1 mile 
bagph = Baguio City, Benguet, Philippines 1 mile 
bak = Bakersfeild, CA 10 mile 
bang = Bangkok, Thailand 1 mile 
bask = Basking Ridge, NJ 1 mile 
beij = Beijing, China 1 mile 
bel = Bellflower, CA 1 mile (also counts as Downey) 
belt = Bell Bethesda, MD 1 mile 
bhp = Bhopal, India 1 mile 
bou = Boulder, CO 1 mile 
bre = Brea, CA 1 mile 
cal = Calabasas, CA 1 mile 
carl = Carlsbad, CA 1 mile
carm = Carmel Valley, CA 1 mile 
che = Chengdu, Suchuan, China 1 mile 
chi = Chino Hillsa, CA 1 mile 
cho = Chongquing, China 1 mile
chu = Chula Vista, CA 1 mile 
cla = Clarksville, MD 1 mile 
cle = Clearlake, CA 1 mile 
clew = Clearwater, FL 1 mile 
col = Colombo, Sri Lanka 1 mile 
colo = Colorado Springs, CO 1 mile 
colum = Colombus, Ohio 1 mile 
con = Concord, CA 1 mile
cor = Coronado, CA 1 mile 
cort = Corte Madera, CA 1 mile 
cup = Cupertino (Monte Vista), CA 1 mile 
dal - Daly City, CA 1 mile 
dan = Danville, CA 1 mile 
dav = Davis, CA 1 mile 
del = Del Mar, CA 
delm = Delmar, NY
den = Denver, CO 
det = Detroit, Michigan 
di = Diamond Bar, CA 
Downey = Bellflower data 
du = Dubai, United Arab Emirates
dub = Dublin, CA
ea = East Oakland, CA 
el = El Centro, CA 
ell = Ellicott, Maryland 
en = Encinitas, CA
ens = Surrey, England (listed as England, Surrey)
fo = Fair Oaks, CA
fx = Fairfax, VA
fa = Fairfeild, CA
fed = Federal Way, WA 
fon = Fontana, CA
for = Fortuna, CA
fre = Freehold, NJ
frem = Fremont, CA 
fres = Fresno, CA
fri = Frisco, TX
ful = Fullerton, CA
ga = Gangnam-gu, Seoul, SK
gay = Gayang-dong, Seoul, SK
ge = GeumJeong-gu, Busan, SK
gl = Glendale, CA
gr = Grass Valley, CA 
gre = Greenfield, CA 
gu = Gurgaon, Haryana, India
hai = Haidian, Beijing, China 
han = Hanford, CA 
ha = Hanoi, Vietnam 
haw = Hawthorne, CA 
hay = Hayward, CA
he = Hercules, CA
her = Hermosa Beach, CA
hern = Herndon, VA 
hi = Hillsborough, CA
ho = Hong Kong
hon = Hongkou, Shanghai, China
hu = Hunan, China
hun = Hung Hom , Hong Kong
hunt = Huntington Beach, CA
hunts = Huntington Station, NY
mo =  Morelia, Michoacn, Mexico
st = Stockholm, Sweden 
im = Imperial Beach, CA
ir = Irvine, CA 
je = Jeju-si, Jeju-do, SK
ji= Jiaozuo, Henan, China  
kai = Kai Ping, China
kat = Katy, TX
ki = Kihei, HI
kla = Klamath Falls, OR
la = La Caada, CA
laf = Lafayette, CA
lak = Lake Forest, WA
lakw = Lakewood, CA
lav = Las Vegas, NV
li = Liaoning, China
lib = Libertyville, IL
liu = Liuzhou, Guangxi, China
liv = Livingston, NJ
lo = Lompoc, CA
lon = Long Beach, CA
los = Los Altos
log = Los Gatos, CA
lub = Lubbock, TX
ma = Makati, Manila, Philippines
mar = Marin County, CA
med = Medina, WA
men = Menlo Park, CA 
mer = Merced, CA
mi = Milpitas, CA
min = Minato, Japan 
mis = Mississauga, Ontario
miz = Mizuhoku, Nagoya, Japan
mok = Mok-dong, Yangcheon-gu, Seoul, SK
mon = Monrovia, CA
mop = Monterey Park, CA
mont = Monterey, CA
mor = Morgan Hill, CA
mori = Morioka, Japan
mrd = Mountain Rd, Newbury NH
mv = Mountain View, CA
muk = Mukilteo, WA 
mum = Mumbai, India
mur = Murrieta, CA
nam = Namyangju-si,Gyeonggi-do,SK 
nan = Nancheng, China 
nanj = Nanjing, Jiangsu, China
nap = Napa, CA
napr = Naperville, IL
new = New Delhi, Delhi, India
newr = New Port Richey, FL
nor = North Hollywood, CA
nort = Norton, MA
nov = Novato, CA
op = Oak Park, CA
oa = Oakland, CA
oak = Oakley, CA
oj = Ojai, CA 
ok = Oksu-dong, SK
ol = Olympia, WA
or = Orange, CA 
orl = Orleans, CA
ory = Oryun-dong, Seoul, South Korea (SK)
ov = Overland Park, KS
ox = Oxnard, CA
pc = Pacific Palisades, CA
pa = Palo Alto, CA 
pave = Palos Verdes Estates, CA
pv = Palos Verdes 
pap = Parsippany, NJ 
pas = Pasadena, CA
pe = Penang, Malaysia 
ph = Phoenix, AZ
pi = Pinole, CA 
pl = Placerville, CA
ple = Pleasanton, CA 
pp = Point Pleasant, NJ
po = Pompano Beach, FL 
pm = Port Moody, Canada 
por = Portland, OR
pr = Port Ridge, NY 
pri = Princeton, NJ
pu = Pune, India
pb = Punjabi Bagh
q = Qingdao, China 
rc = Rancho Cordova, CA 
rcu = Rancho Cucamonga, CA
Rancho Palos Verdes = Palos Verdes 
re = Redlands, CA
rw = Redwood City, CA
ri = Riverside, CA
rob = Robbinsdale, MN 
roc = Rocklin, CA
rod = Rodeo, CA 
sac = Sacramento, CA
sm = Salem, IL
sld = Salida, CA
sln = Salinas, CA
slc = Salt Lake City UT
sbr = San Bernardino, CA 
sc = San Carlos, CA
scc = San Clemente, CA 
sfr = San Fernando, CA
sf = San Francisco 
sg = San Gabriel, CA
sj = San Jose, CA 
sl = San Leandro, CA 
slor = San Lorenzo, CA 
slb = San Luis Obispo
smr = San Marcos, CA
smt = San Mateo, CA
sp = San Pablo, CA 
spe = San Pedro, CA
sr = San Rafael, CA
srm = San Ramon, CA
sb = Santa Barbara, CA 
scl = Santa Clarita, CA 
scr = Santa Cruz, CA 
sma = Santa Maria 
smo = Santa Monica, CA 
sro = Santa Rosa, CA 
san = Santee, CA
sant = Santpoort-Noord, Netherlands
spb = Sao Paulo, Brazil 
sar = Saratoga, CA
sau = Saugua, CA
seb = Sebastopol, CA
sha = Shanghai, China
shap = Shapingba, China
she = Shenzhen, China







# Comparing NDVI Values and Frequencies Across Locations 


## Saving the NDVI Values as integers, converting the rasters to vector matrixes, and creating single data drames 
```{r, warning= FALSE}
#save data as integers 
writeRaster(x = naip_ndvi_br5,
            # where your file will go - update with your file path!
            
            filename="~/final-individual-getlaam/NDVIcomglombr.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S', 
            overwrite=TRUE) 
# convert the raster to vector/matrix ('getValues' converts the RasterLAyer to array) )
nr_br5 <-getValues(naip_ndvi_br5)
str(nr_br5)

writeRaster(x = naip_ndvi_br1,
            filename="~/final-individual-getlaam/NDVIcomglombr1.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S',
            overwrite=TRUE) 
nr_br1 <-getValues(naip_ndvi_br1)

str(nr_br1)

writeRaster(x = naip_ndvi_hkhk,
            filename="~/final-individual-getlaam/NDVIcomglomhkhk.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S',
            overwrite=TRUE) 
nr_hkhk <-getValues(naip_ndvi_hkhk)
str(nr_hkhk)
writeRaster(x = naip_ndvi_mp,
            filename="~/final-individual-getlaam/NDVIcomglommp.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S',
            overwrite = TRUE) 
nr_mp <-getValues(naip_ndvi_mp)
str(nr_mp)
writeRaster(x = naip_ndvi_np,
            filename="~/final-individual-getlaam/NDVIcomglomnp.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S',
            overwrite = TRUE) 
nr_np <-getValues(naip_ndvi_np)
str(nr_np)
writeRaster(x = naip_ndvi_rm,
            filename="~/final-individual-getlaam/NDVIcomglomrm.tif", 	
            format = "GTiff", 					# save as a tif
            datatype = 'INT2S',
            overwrite = TRUE) 
nr_rm <-getValues(naip_ndvi_rm)
str(nr_rm)
```

\newpage

# Creating the data frames for each location
```{r}
data_empty<- data.frame() 

data_rome<- as_tibble(nr_rm) %>% mutate (place="Rome, Italy")

data_newport<- as_tibble(nr_np)%>% mutate(place="Newport Beach, CA")

data_manila<- as_tibble(nr_mp)%>% mutate(place="Manila, Phillippines")
\
data_hongkong<- as_tibble(nr_hkhk)%>% mutate(place="Hong Kong, Hong Kong")

data_berkeley<- as_tibble(nr_br)%>% mutate(place= "Berkeley, CA 5 mile")

data_berkeley1<- as_tibble(nr_br1)%>% mutate(place= "Berkeley, CA")

NDVIcombined<- bind_rows(data_rome, data_newport, data_manila, data_hongkong,data_berkeley, data_berkeley1 )

NDVIcombined%>% group_by(place)%>% summarize(mean_value= mean(value, na.rm= TRUE))
```
\newpage

# Plotting NDVI Values by site for a visual comparison 
```{r fig.height= 10, fig.width=20, comment= FALSE} 
    ggplot(NDVIcombined, aes(x= value, fill= place)) +
    geom_histogram(position = "dodge")+
    ggtitle("Picture Derived NDVI - All Sites, Dodge Histogram") +
    xlab("NDVI Values") + ylab("Frequency: Number of Occurances") +
    theme(text = element_text(size=20))
  
```
\newpage
```{r fig.height=13, fig.width= 15}
    ggplot(NDVIcombined, aes(x= value, fill= place)) +
    geom_density(alpha = 0.3)+
    ggtitle("Picture Derived NDVI - All Sites, Density Histogram") +
    xlab("NDVI Values") + ylab("Frequency") +
    theme(text = element_text(size=20))
```
\newpage
```{r, fig.height=10, fig.width= 15}
    ggplot(NDVIcombined, aes(x= value, fill= place)) +
    geom_histogram(position = "dodge")+
    ggtitle("Picture Derived NDVI - All Sites") +
    xlab("NDVI Values") + ylab("Frequency: Number of Occurances") +
    theme(text = element_text(size=20))+
      facet_wrap(~place)
```